---
title: "AIOI tidying"
author: "Ian Douglas"
date: "4/3/2019"
output: html_document
---
AIOI tidying AND scoring script

```{r}
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/AIOI raw.csv", stringsAsFactors = FALSE)
```
#View the first rows of the ID column
```{r}
df$Q4[1:20]
```
#Looks that mock/test data ends at line 9 (though "1111" is also test data)
#Extract desired data
```{r}
#retain the timestamp from Qualtrics
df1 <- df[-c(1:9,12),] %>% select(RecordedDate, starts_with("Q"))
```
#clean the subject IDs
```{r}
#extract digits within subject ID field and evaluate output
where.na(df1)[2]
quantity.missing(df1)[2]
test<-mutate(df1, 
             Q4 = as.integer(str_extract(df1$Q4,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q4)
which(is.na(test)==TRUE)
which(test==0)
```
###Conclusion: subject IDs all contain (at least one) non-zero digit(s)
```{r}
#Search for duplicate entries
digits<-mutate(df1, 
             Q4 = as.integer(str_extract(df1$Q4,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q4)
#then define "dup"
dup <- which(duplicated(digits$Q4))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q4==digits$Q4[dup[i]]))),
                      df1$Q4[which(digits$Q4==digits$Q4[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup))), 
                ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q4==digits$Q4[dup[i]]))),
                 as.character(df1$RecordedDate[which(digits$Q4==digits$Q4[dup[i]])]))
}
View(cbind(duplicates,dates))
# search <- cbind(as.data.frame(duplicates),
#                 as.data.frame(dates))[,c(4,9,5,10)]
# names(search) <- c("raw entry #1", "timestamp1","raw entry #2","timestamp2")
# search
```
#Create a dataframe of these duplicates to analyze response patterns
```{r}
vec <- vector()
for (i in unique(as.vector(digits[,1])[dup])) {
    vec <- c(vec,c(which(digits == i)))
}
dup.view <- df1[vec,]
dup.view$df1.indices <- vec

####View(dup.view)

# subject ID        index to rm
# “007p” 		        3, 5
# “EL046”		          29
# “ELO051P”		        33
# “EL006P”		none [recode next entry]
# “elo6lp”		none [recode this typo]
# “EL079P”		        45
# “El071P”		        53
# “el088p”		        57
# “ELO96P”		        66
# “el140”		        96,97
# ————————
# question: EL127p ???
# library(haven)
# #convert all fields to character for csv and sav write-out
# aioi.duplicates <- as.data.frame(lapply(dup.view[,1:ncol(dup.view)], function(x) as.character(x)),
#                      stringsAsFactors = F)
# write.csv(aioi.duplicates, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/aioi_duplicates.csv", row.names = FALSE)

```
#remove the identified duplicates from the search procedure
```{r}
#First, recode the typo so that EL006 doesn't appear to be duplicated
df1[which(df1$Q4 == "elo6lp"), "Q4"] <- "EL061"
rm <- c(3,5,29,33,45,53,57,66,86,96,97)
#remove these rows from the data
df2 <- df1[-rm,]
```
#Standardize the subject IDs
```{r}
df3 <- ELFK.identsubid(df2, "Q4")
```
#check to make sure there are not duplicates:
```{r}
nrow(df3) == length(unique(df3$Q4))
```
#Search for the answer to question 1, amidst the many entries therein
```{r}
#We need to search for and retain the numbers 1 and 2 that are entered
#in the column with highest number
AIOI_P1_EDU <- apply(df3[3:11], 1, function(x) max(grep("1",x)))
AIOI_P2_EDU <- apply(df3[3:11], 1, function(x) max(grep("2",x)))
#some did not have a 2, so the max() arg created "-Inf", so recode this
#Ignore the warnings from R say this created -Inf
AIOI_P2_EDU[grepl("-Inf",AIOI_P2_EDU)] <- NA_integer_
#Interpret the "Other" (column 9 was selected)
other.txt1<-df3$Q5[which(AIOI_P1_EDU==9)]
other.txt2<-df3$Q6[which(AIOI_P2_EDU==9)]
#results show nothing was entered in the corresponding text field.
#take the second highst entry for each of these cases.
replacements <- c(6,8,4)
to.replace <- c(which(AIOI_P1_EDU==9))
for (i in 1:3) {
  AIOI_P1_EDU[to.replace[i]] <- replacements[i]
}
AIOI_P2_EDU[43] <- 8

#these relative column positions are the codes from 1 to 8 corresponding to education level for each parent. Add this to the dataframe and remove the other qualtrics output
df4 <- cbind(df3[,1:2],AIOI_P1_EDU,AIOI_P2_EDU,df3[,14:ncol(df3)])
#ignore error messages "no non-missing arguments to max; returning -Inf""
```
#extract numbers from the income field
```{r}
#first remove the punctuation, spaces, and dollar signs
rm.characters <- function(expr1, expr2, expr3, 
                          expr4, expr5,expr6, 
                          expr7, string) {
  #Step1: remove punctuation, spaces, and dollar signs
  string <- gsub(expr1, "", string) 
  string <- gsub(expr2, "", string)
  string <- gsub(expr3, "", string)
  string <- gsub(expr4, "", string)
  string <- gsub(expr5, "", string)
  string <- gsub(expr6, "", string)
  string <- gsub(expr7, "", string)
  #if K was entered, it means thousand
  string <- gsub("k", "000", string)
  string <- gsub("K", "000", string)
  string <- gsub("m", "000", string) #this was a typo meaning thousand, not million
  #Step2: replace blanks with NA
  
  string[which(string == "")] <- NA_integer_
  
  string <- as.integer(string)
  return(string)
}
new.Q3_2 <- rm.characters(" ", "\\$", ",", "[.]$","\\?","[+]","[>]",
                          df4$Q3_2)
#Ignore error message "NAs introduced by coercion"
```
#do the same for the second parent income column
```{r}
rm.char2 <- function(string) {
  x <- string
  #delete everything after the decimal point
  x <- gsub("\\..*","",x)
  #zeros that come after spaces need to be changed to just "0"
  x <- gsub(" 0","0",x)
  #delete alphabetical strings that come after spaces (delete comments)
  #replace K, k with 000 to represent thousands
  x <- gsub("k", "000", x)
  x <- gsub("K", "000", x)
  #Remove $ + , >
  x <- gsub("\\$","",x)
  x <- gsub(",","",x)
  x <- gsub("[>]","",x)
  x <- gsub("[+]","",x)
  x <- as.integer(x)
  x <- as.integer(x)
  return(x)
  #ignore error messages
}
new.Q3_4 <- rm.char2(df4$Q3_4)
#ignore error messages "NAs introduced by coercion"
```
#cobine the new and old columns into a new df with desired columns only
```{r}
df5 <- cbind(df4[1:5],new.Q3_2,df4[7],new.Q3_4)
```
#reformat the date
```{r}
df6 <- df5 %>% 
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```
#recode the income variables
```{r}
#first cut each into appropriate categories, then recode them
cats1 <- cut(new.Q3_2, breaks = c(0,10000,25000,40000,
                                  55000,75000,85000,100000,
                                  150000, 200000, Inf))
cats2 <- cut(new.Q3_4, breaks = c(0,10000,25000,40000,
                                  55000,75000,85000,100000,
                                  150000, 200000, Inf))
levels <- levels(cats1) #same for both lists
cats1.recode <- recode(cats1, 
                       "(0,1e+04]"="1", "(1e+04,2.5e+04]"="2",
                       "(2.5e+04,4e+04]"="3","(4e+04,5.5e+04]"="4",
                       "(5.5e+04,7.5e+04]"="5", "(7.5e+04,8.5e+04]"="6",
                       "(8.5e+04,1e+05]"="7", "(1e+05,1.5e+05]"="8",
                       "(1.5e+05,2e+05]"="9", "(2e+05,Inf]"="10")
cats2.recode <- recode_factor(cats2, 
                       "(0,1e+04]"="1", "(1e+04,2.5e+04]"="2",
                       "(2.5e+04,4e+04]"="3","(4e+04,5.5e+04]"="4",
                       "(5.5e+04,7.5e+04]"="5", "(7.5e+04,8.5e+04]"="6",
                       "(8.5e+04,1e+05]"="7", "(1e+05,1.5e+05]"="8",
                       "(1.5e+05,2e+05]"="9", "(2e+05,Inf]"="10")
parent1.income <- as.numeric(as.character(cats1.recode))
parent2.income <- as.numeric(as.character(cats2.recode))
```
#add correct variable names
```{r}
v.names <- c("AIOI_DATE_COMPLETE", "IDENT_SUBID", 
             "AIOI_P1_EDU","AIOI_P2_EDU",
             "AIOI_P1_Occupation","AIOI_P1_Income",
             "AIOI_P2_Occupation","AIOI_P2_Income"
             )
names(df6) <- v.names
```
#insert the recded income variables
```{r}
df6$AIOI_P1_Income <- parent1.income
df6$AIOI_P2_Income <- parent2.income
```
#write out finalized data
```{r}
write_rds(df6,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/AIOI.rds")
#Convert to character before writing out .csv and .sav
library(haven)
df7<-as.data.frame(lapply(df6,as.character),stringsAsFactors=F)
write.csv(df7, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/csv/AIOI_final.csv", row.names = FALSE)
write_sav(df7, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/SPSS/AIOI_final.sav")
```
