---
title: "FQ tidying"
author: "Ian Douglas"
date: "5/20/2019"
output: html_document
---
#load raw data, extracted 5/15/2019
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/FQ raw.csv", stringsAsFactors = FALSE)
```

View subj ID column to identify fake data
```{r}
head(df$Q26) #delete the first three rows
tail(df$Q26) #last row contains fake data
```
Delete the first two row
```{r}
df1 <- df[-1:-2,] %>% select(RecordedDate, starts_with("Q"))
```
#search for duplicates in the id column
```{r}
id.search(df1, "Q26","RecordedDate")
```

There are 4 duplicates to assess.
-EL104: take the first entry (consistent with Michelle V's suggestion)
-EL144: the first entry is actually the sibling EL145
-EL040: delete first entry due data missingness
-EL050: take the first entry (consistent with Michelle V's suggestion)
```{r}
df1$Q26[which(df1$Q26 == "EL144" & df1$RecordedDate == "2018-06-12 17:20:20")] <- "EL145"
omit <- c(
  which(df1$Q26 == "EL104" & 
          df1$RecordedDate == "2018-06-04 17:56:56"),
  which(df1$Q26 == "EL040" & 
          df1$RecordedDate == "2018-05-21 10:15:38"),
  which(df1$Q26 == "EL050" & 
          df1$RecordedDate == "2018-08-09 14:07:42")
)
df2<-df1[-omit,]
```

#Format the data
```{r}
df3 <- format.date(df2, "RecordedDate")
```
#Standardize the subject IDs
```{r}
df4 <- ELFK.identsubid(df3, "Q26")
```
#Convert variables to numeric
```{r}
#As per Michelle L's note, replace 3 ages that were entered as words (not numbers), with their numeric equivalant, before altering datatype
df4[which(df4$Q26 %in% c("EL099","EL097", "EL127")),"Q22"] <- c(14,
                                                                14,
                                                                6)
df5 <- df4 %>% mutate_at(c(3:7, 9:18, 21:23), as.numeric)
```

#attach the variable names
```{r}
vnam <- c("FQ_DATE_COMPLETE", "IDENT_SUBID", "FQ_1", "FQ_2", 
          "FQ_3", "FQ_4","FQ_5","FQ_5_OTHER","FQ_6","FQ_7", 
          "FQ_8A", "FQ_8B", "FQ_9", "FQ_10", "FQ_11", "FQ_12", 
          "FQ_13", "FQ_14", "FQ_15", "FQ_16", "FQ_17", "FQ_18",
          "FQ_19", "FQ_20", "FQ_21")
names(df5) <- vnam
```

#For select numeric variables, NA should be coded 0
```{r}
here<-which(
  names(df5) %in% c("FQ_1", "FQ_2", "FQ_3","FQ_4", 
                    "FQ_6","FQ_7", "FQ_9","FQ_10",
                    "FQ_13","FQ_14")
  )

df6 <- df5 %>% mutate_at(here, 
                         function(x) ifelse(is.na(x), 0, x))
```
Recode some variables that output differently from Qualtrics
```{r}
rm(list="here")
#FQ_8A: 1 = YES, 2 = NO; change 2 to 0 for NO
#FQ_11: 1 = YES, 2 = NO; change 2 to 0 for NO
#FQ_12: 1 = YES, 2 = NO; change 2 to 0 for NO
here <- which(
  names(df5) %in% c("FQ_8A", "FQ_11", "FQ_12")
  )
df7 <- df6 %>% mutate_at(here, function(x) ifelse(x ==2,0,x))
```

#Further recoding
If there was something entered in 8B, then 8A should have been entered as 1. Change cases where this is not the case.
```{r}
df7$FQ_8A[!is.na(df7$FQ_8B)] <- 1
#likewise, if 8B is NA, 8A should be zero
all(df7$FQ_8A[is.na(df7$FQ_8B)] == 0) #TRUE
```
Create a new column that binarizes the text enries from question 21
```{r}
#using Michelle L's notes, the text entries were intrepreted as follows:
cases<-c("EL101","EL109","EL110","EL108","EL119","EL127",
         "EL132","EL138","EL143","EL135","EL104","EL041",
         "EL042","EL058","EL059","EL147","EL146","EL144","EL060")
FQ_21_binary <- rep(0, length.out = nrow(df7))
FQ_21_binary[df7$IDENT_SUBID %in% cases] <- 1
df8 <- df7
df8$FQ_21_UNUSUAL <- FQ_21_binary
```
#Re-code the age to months
```{r}
df8$FQ_18 <- df8$FQ_18*12
```
#Done!
Write out the tidy data
```{r}
saveRDS(df8,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/R/FQ_tidy.rds")
```
#Write out scored data, as there are no further variables to code!
```{r}
saveRDS(df8,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/FQ_scored.rds")
```

