---
title: "PQ tidying"
author: "Ian Douglas"
date: "5/30/2019"
output: html_document
---
#load in raw data
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/PQ raw.csv", stringsAsFactors = FALSE)
```
#View the ID field to examine fake/test ddata
```{r}
df$Q1[1:10] #real entries begin on line 2
tail(df$Q1) #no fake data
```
#Extract desired data
```{r}
df1 <- df[-1:-2,] %>% dplyr::select(RecordedDate, starts_with("Q"))
```
#Search for duplicates in theID field
```{r}
#First see, if any entries contain all letters
where<-all.letters(df1$Q1)
# [1] 23
df2 <- df1[-where,]#remove the entry
View(id.search(df2, "Q1", "RecordedDate"))
```
#index entries to delete
```{r}
ids.to.remove <- c(
  which(df2$Q1 == "097" & df2$RecordedDate == "2017-05-30 11:30:18"), #missingness
  which(df2$Q1 == "El122" & df2$RecordedDate == "2018-05-03 17:03:35"), # missingness
  which(df2$Q1 == "EL104" & df2$RecordedDate == "2018-06-13 17:45:17"),#missingness
  which(df2$Q1 == "EL105" & df2$RecordedDate == "2018-06-13 17:46:31")
)
#FIRST:
#take the last three columns from the above entry and merge it with the correct one.
df2[which(df2$Q1 == "EL105" & df2$RecordedDate == "2018-05-29 16:31:25"), 22:25] <-
df2[which(df2$Q1 == "EL104" & df2$RecordedDate == "2018-06-13 17:45:17"), 22:25]
#Next, delete the unwanted rows
df3 <- df2[-ids.to.remove,]
#lastly, swith the subject ID for 104 and 105, whose (retained) entries switched the subject ID
df3$Q1[c(grep("104", df3$Q1),grep("105", df3$Q1))] <- c("EL105", "EL104")
```
#Format subject ID and date columns
```{r}
df4 <- df3 %>% ELFK.identsubid("Q1") %>% format.date("RecordedDate")
```
#Add in the variable names
```{r}
#first create an empty column
df5 <- data.frame(df4[1:5],"PQ_3_AGEFOSTER" = NA_integer_, df4[6:ncol(df4)])
#create the list of variable names in the correct order
vnam <- c("PQ_DATE_COMPLETE", "IDENT_SUBID",
          "PQ_1_COUNTRYBORN", "PQ_2_CITYBORN", "PQ_3_AGEORPH", 
          "PQ_3_AGEFOSTER","PQ_4_AGEADOPT","PQ_5_GENHEALTHADOPT",
          "PQ_6A_GROCHART","PQ_6B_PERCENTILE","PQ_7A_HEALTHCONS",
          "PQ_7B_EXPLAN","PQ_8A_BEHCONS","PQ_8B_EXPLAN",
          "PQ_9_STRENGTH", "PQ_10A_HEALTHCONS_OVERC", "PQ_10B_EXPLAN",
          "PQ_11A_BEHACONS_OVERC","PQ_11B_EXPLAN","PQ_12A_OTHERCHILD",
          "PQ_12B_AGEOTHERCH","PQ_12C_ADOPTORBIOCH","PQ_13_MOTIVADOPT",
          "PQ_14A_TALKADOSTORY","PQ_14B_CHENJOYADSTORY","PQ_14C_PENJOYADSTORY")
names(df5) <- vnam
```
#For select subjects
merge in their data from older versions of the form, using Michelle L's notes.
```{r}
# index.5 <- Parent_Q.3$IDENT_SUBID[index.5]
# index.6 <- Parent_Q.3$IDENT_SUBID[index.6]
# index.7 <- Parent_Q.3$IDENT_SUBID[index.7]
# index.13 <- Parent_Q.3$IDENT_SUBID[index.13]
# index.14 <- Parent_Q.3$IDENT_SUBID[index.14]
# index.16 <- Parent_Q.3$IDENT_SUBID[index.16]
# index.17 <- Parent_Q.3$IDENT_SUBID[index.17]
# index.18 <- Parent_Q.3$IDENT_SUBID[index.18]
# index.19 <- Parent_Q.3$IDENT_SUBID[index.19]
# index.22 <- Parent_Q.3$IDENT_SUBID[index.22]

for (i in 1:length(index.5)) { #5
  df5$PQ_3_AGEORPH[which(df5$IDENT_SUBID == index.5[i])] <- 
  Parent_Q.3$PQ_3_AGEORPH[Parent_Q.3$IDENT_SUBID == index.5[i]]
}

for (i in 1:length(index.6)) { #6
  df5$PQ_3_AGEFOSTER[which(df5$IDENT_SUBID == index.6[i])] <- 
  Parent_Q.3$PQ_3_AGEFOSTER[Parent_Q.3$IDENT_SUBID == index.6[i]]
} 

for (i in 1:length(index.7)) { #7
  df5$PQ_4_AGEADOPT[which(df5$IDENT_SUBID == index.7[i])] <- 
  Parent_Q.3$PQ_4_AGEADOPT[Parent_Q.3$IDENT_SUBID == index.7[i]]
} 

for (i in 1:length(index.13)) { #13
  df5$PQ_8A_BEHCONS[which(df5$IDENT_SUBID == index.13[i])] <- 
  Parent_Q.3$PQ_8A_BEHCONS[Parent_Q.3$IDENT_SUBID == index.13[i]]
}

for (i in 1:length(index.14)) { #14
  df5$PQ_8B_EXPLAN[which(df5$IDENT_SUBID == index.14[i])] <- 
  Parent_Q.3$PQ_8B_EXPLAN[Parent_Q.3$IDENT_SUBID == index.14[i]]
}

for (i in 1:length(index.16)) { #16
  df5$PQ_10A_HEALTHCONS_OVERC[which(df5$IDENT_SUBID == index.16[i])] <- 
  Parent_Q.3$PQ_10A_HEALTHCONS_OVERC[Parent_Q.3$IDENT_SUBID == index.16[i]]
}

for (i in 1:length(index.17)) { #17
  df5$PQ_10B_EXPLAN[which(df5$IDENT_SUBID == index.17[i])] <- 
  Parent_Q.3$PQ_10B_EXPLAN[Parent_Q.3$IDENT_SUBID == index.17[i]]
}

for (i in 1:length(index.18)) { #18
  df5$PQ_11A_BEHACONS_OVER[which(df5$IDENT_SUBID == index.18[i])] <- 
  Parent_Q.3$PQ_11A_BEHACONS_OVER[Parent_Q.3$IDENT_SUBID == index.18[i]]
}

for (i in 1:length(index.19)) { #19
  df5$PQ_11B_EXPLAN[which(df5$IDENT_SUBID == index.19[i])] <- 
  Parent_Q.3$PQ_11B_EXPLAN[Parent_Q.3$IDENT_SUBID == index.19[i]]
}

for (i in 1:length(index.22)) { #22
  df5$PQ_12C_ADOPTORBIOCH[which(df5$IDENT_SUBID == index.22[i])] <- 
  Parent_Q.3$PQ_12C_ADOPTORBIOCH[Parent_Q.3$IDENT_SUBID == index.22[i]]
}
```


#recode the following questions, which qualtrics coded incorrectly.
```{r}
var.indices <- c(grep("_6A_",names(df5)),
                 grep("_7A_",names(df5)),
                 grep("_8A_",names(df5)),
                 grep("_10A_",names(df5)),
                 grep("_11A_",names(df5)),
                 grep("_12A_",names(df5)),
                 grep("_14A_",names(df5)),
                 grep("_14B_",names(df5)),
                 grep("_14C_",names(df5)))

df5[var.indices] <- lapply(df5[var.indices], function(x) as.numeric(sub(2,0,x)))
```
#Convert the ages of the friends to months
```{r}
df5$PQ_12B_AGEOTHERCH <- gsub("([A-z])", "", df5$PQ_12B_AGEOTHERCH)
df5$PQ_12B_AGEOTHERCH<- strsplit(as.character(df5$PQ_12B_AGEOTHERCH), ",")


#convert to numeric, multiply by 12 to convert to months
for (ii in 1:length(df5$PQ_12B_AGEOTHERCH)){
  df5$PQ_12B_AGEOTHERCH[[ii]]<- as.numeric(df5$PQ_12B_AGEOTHERCH[[ii]])
  df5$PQ_12B_AGEOTHERCH[[ii]]<- df5$PQ_12B_AGEOTHERCH[[ii]]*12
  df5$PQ_12B_AGEOTHERCH[[ii]]<- paste(df5$PQ_12B_AGEOTHERCH[[ii]], collapse=",")} 
#unlist 
df5$PQ_12B_AGEOTHERCH <- unlist(df5$PQ_12B_AGEOTHERCH)
```
According to Michelle L's notes, make one further correction required:
```{r}
df5[df5$IDENT_SUBID == "EL127", "PQ_12B_AGEOTHERCH"] <- "228"
#Fix on additional error that the above script created
df5[df5$IDENT_SUBID == "EL139", "PQ_12B_AGEOTHERCH"] <- "120,180"
```
#Finally, convert necessary columns to correct numeric data type
```{r}
select.vars <- c(5,6,7,8,9,11,13,16,18,20,22,24:ncol(df5))
df5[select.vars] <- lapply(df5[select.vars],as.numeric)
```

Done!
No scoring for this form, write out finalized data
```{r}
saveRDS(df5, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PQ.rds")
```

