---
title: "BDI scoring"
author: "Ian Douglas"
date: "6/3/2019"
output: html_document
---
#load in tidy data
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(tidyverse))
df<-readRDS("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/bdi_tidy.rds")
```
#Create sum scores, sperately w.r.t. BDI-1A and BDI-2
###BDI-1A
####Exclude questions 9, 11 and 22, pertaining to weight gain and prolonged sleep, respectively.
```{r}
df1 <- df %>%
  group_by(IDENT_SUBID) %>%
  mutate(PARENT_BDI1A_SUM = mean(c(PARENT_BDI1A_1,PARENT_BDI1A_2,PARENT_BDI1A_3,
                                   PARENT_BDI1A_4,PARENT_BDI1A_5,PARENT_BDI1A_6,
                                   PARENT_BDI1A_7,PARENT_BDI1A_8,PARENT_BDI1A_10,
                                   PARENT_BDI1A_12,PARENT_BDI1A_13,PARENT_BDI1A_14,
                                   PARENT_BDI1A_15,PARENT_BDI1A_16,PARENT_BDI1A_17,
                                   PARENT_BDI1A_18,PARENT_BDI1A_19,PARENT_BDI1A_20,
                                   PARENT_BDI1A_21), na.rm = TRUE)*19)
```
###BDI-2
####Question 9 is already excluded from the raw items
```{r}
df2 <- df1 %>%
  #group_by(IDENT_SUBID) %>%
  mutate(PARENT_BDI2_SUM = mean(c(
    PARENT_BDI2_1,PARENT_BDI2_2,PARENT_BDI2_3,PARENT_BDI2_4,PARENT_BDI2_5,
    PARENT_BDI2_6,PARENT_BDI2_7,PARENT_BDI2_8,PARENT_BDI2_10,PARENT_BDI2_11,
    PARENT_BDI2_12,PARENT_BDI2_13,PARENT_BDI2_14,PARENT_BDI2_15,PARENT_BDI2_16,
    PARENT_BDI2_17,PARENT_BDI2_18,PARENT_BDI2_19,PARENT_BDI2_20,PARENT_BDI2_21), 
    na.rm = TRUE)*20) %>%
  ungroup()
```
#compute a mean score for each as well.
```{r}
df3 <- df2 %>%
  group_by(IDENT_SUBID) %>%
  mutate(PARENT_BDI1A_MEAN = mean(c(PARENT_BDI1A_1,PARENT_BDI1A_2,PARENT_BDI1A_3,
                                   PARENT_BDI1A_4,PARENT_BDI1A_5,PARENT_BDI1A_6,
                                   PARENT_BDI1A_7,PARENT_BDI1A_8,PARENT_BDI1A_10,
                                   PARENT_BDI1A_12,PARENT_BDI1A_13,PARENT_BDI1A_14,
                                   PARENT_BDI1A_15,PARENT_BDI1A_16,PARENT_BDI1A_17,
                                   PARENT_BDI1A_18,PARENT_BDI1A_19,PARENT_BDI1A_20,
                                   PARENT_BDI1A_21), na.rm = TRUE)) %>%
  mutate(PARENT_BDI2_MEAN = mean(c(
    PARENT_BDI2_1,PARENT_BDI2_2,PARENT_BDI2_3,PARENT_BDI2_4,PARENT_BDI2_5,
    PARENT_BDI2_6,PARENT_BDI2_7,PARENT_BDI2_8,PARENT_BDI2_10,PARENT_BDI2_11,
    PARENT_BDI2_12,PARENT_BDI2_13,PARENT_BDI2_14,PARENT_BDI2_15,PARENT_BDI2_16,
    PARENT_BDI2_17,PARENT_BDI2_18,PARENT_BDI2_19,PARENT_BDI2_20,PARENT_BDI2_21), 
    na.rm = TRUE))
```

#Now compute a z-score for each participant's mean
```{r}
mean.bdi1a <- mean(df3$PARENT_BDI1A_MEAN, na.rm = TRUE)
sd.bdi1a <- sd(df3$PARENT_BDI1A_MEAN, na.rm = TRUE)
mean.bdi2 <- mean(df3$PARENT_BDI2_MEAN, na.rm = TRUE)
sd.bdi2 <- sd(df3$PARENT_BDI2_MEAN, na.rm = TRUE)
df4 <- df3 %>% group_by(IDENT_SUBID) %>%
  mutate(PARENT_BDI_Z = ifelse(
    is.na(PARENT_BDI2_MEAN),
    ((PARENT_BDI1A_MEAN - mean.bdi1a)/sd.bdi1a),
    ((PARENT_BDI2_MEAN - mean.bdi2)/sd.bdi2))
    ) %>%
  ungroup()
```
#Finally, replace NaN with NA to enhance accessibility with other software
```{r}
df5 <- df4 %>%
  mutate_at(c(grep("_MEAN",names(df4)),grep("_SUM",names(df4))),
            function(x) replace(x, is.nan(x), NA)) %>%
  mutate_at(c(grep("_MEAN",names(df4)),grep("_SUM",names(df4))),
            function(x) as.numeric(as.character(x)))
```

#Done!
Write out finalized data.
```{r}
saveRDS(df5,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/bdi_final.rds")
```

