---
title: "ELFK Merging"
author: "Ian Douglas"
date: "6/7/2019"
output: html_document
---

# Intro 1: clear environment
```{r}
rm(list=ls())
```

# Intro 2: Define required functions:
```{r}
#########################################
# ELFK.identsubid()                     #
#---------------------------------------#
#Standardize subject ID numbers for ELFK#
#---------------------------------------#
#***Returns a new dataframe!            #
#########################################

ELFK.identsubid <- function(data, id.variable.name) {
  if (class(id.variable.name) != "character") {
    stop("variable names must be character strings")
  } else {
    i <- which(names(data)==id.variable.name)
    tmp.df <- as.character(data[,i])
    tmp.df2<- data %>% 
      mutate_at(i, 
                function(x) as.integer(str_extract(x,pattern ="\\(?[0-9,.]+\\)?"))) %>% 
      mutate_at(i, 
                function(x) paste0(ifelse(nchar(x)==1,
                                          "EL00",ifelse(nchar(x)==2,
                                                        "EL0","EL")),x))
  }
  return(tmp.df2)
  
}

#####################################################################
#Extract, from a vector of values, the entire value that contains a # 
# given regular expression. Like grep() or grepl(), but returns     #
# the value, not its index or TRUE/FALSE indicator                  # 
#####################################################################
#-------------------------------------------------------------------#
extr <- function(value, vector) {
  out <- vector[grep(value,vector)]
  return(out)
}
```

# 1: Load all finalized qualtrics forms
```{r}
q1 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/AIOI.rds")
q2 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/bdi_final.rds") #bdi1 adn bdi2 in wide form together
q3 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/CQ final.rds")
q4 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/DSM_C final.rds")
q5 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/DSM_P scored.rds")
q6 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/final_cbcl.rds")
q7 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/FQ_scored.rds")
q8 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/Grit_Child.rds")
q9 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/Grit_Parent.rds")
q10 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/IAI.rds")
q11 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/IF_final.rds")
q12 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/Motivation.rds")
q13 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PPDS_fem_child.rds")
q14 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PPDS_fem_parent.rds")
q15 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PPDS_mal_child.rds")
q16 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PPDS_mal_parent.rds")
q17 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/PQ.rds")
q18 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/RADS_scored.rds")
q19 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/RPQ_scored.rds")
q20 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/SCARED.rds")
q21 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/SS.rds")
q22 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/STAI_state_scored.rds")
q23 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/STAI_trait_scored.rds")
q24 <- readRDS("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/CRPR_final.rds")
```

##data cleaning
```{r}
#ensure that all IDENT_SUBID are exactly identical across forms, to avoid duplicates
for (i in 1:23) {
  assign(paste("df", i, sep = ""),(getElement(.GlobalEnv, paste("q", i, sep = "")) %>%
    ungroup() %>% mutate_at("IDENT_SUBID", function(x) trimws(as.character(x)))),
    envir = .GlobalEnv)
}
#Next, since PQ_6A_GROCHART was used in the computation of an IAI variable, it is going to be duplicated during the merge. Delete it from the IAI
df10 <- df10 %>% select(-PQ_6A_GROCHART)
#create master list of suject IDs
master.id.list <- c()
for (i in 1:23) {
  master.id.list <- c(master.id.list,
                      unlist(getElement(
                        .GlobalEnv, paste("df", i, sep = "")
                        )[, "IDENT_SUBID"]))
}
master.id.list <- trimws(unique(master.id.list))
#remove "NANA" from master.id.list
master.id.list <- master.id.list[-which(master.id.list=="NANA")]
```

##merge them all
```{r}
df.merge <- data.frame("IDENT_SUBID" = master.id.list) #start with a list of all IDs
for (i in 1:23) { #merge all the others into it
  df.merge <- merge(df.merge, getElement(
    .GlobalEnv, paste("df", i, sep = "") #pull data frame from global environment
    ), by = "IDENT_SUBID", all = TRUE) #merge using "IDENT_SUBID"
}
```

IF "any(duplicated(df.merge$IDENT_SUBID))" is "TRUE", then run the following. IF not skip.
```{r}
# duped <- df.merge[df.merge$IDENT_SUBID %in% df.merge$IDENT_SUBID[which(duplicated(df.merge$IDENT_SUBID))],]
# set1 <- duped[1:2,]
# set2 <- duped[3:4,]
# set3 <- duped[5:6,]
# # set4 <- duped[7:8,]
# # set5 <- duped[9:10,]
# # set6 <- duped[11:12,]
# # set7 <- duped[13:14,]
# set.list <- list(set1, set2, set3)
# tf.matrix <- matrix(rep(NA,length.out= 3*555),ncol = 555,
#                     dimnames = list(c(set1$IDENT_SUBID[1],set2$IDENT_SUBID[1],
#                          set3$IDENT_SUBID[1]),names(duped)))
# 
# for (i in 1:length(set.list)) {
#   for (j in 1:555) {
#     tf.matrix[i,j] <- !identical(
#       as.vector(unlist(set.list[[i]][j])[1]),as.vector(unlist(set.list[[i]][j])[2])
#       )
#   }
# }
# apply(tf.matrix,1,which)
```


##write out csv and rds files
```{r}
saveRDS(df.merge, "/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/R/Qualtrics data.rds")
#convert all to character for .csv write-out to increase compatibility
qualtrics.data <- df.merge
qualtrics.data[] <- lapply(qualtrics.data, as.character)
write.csv(qualtrics.data, "/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/csv/qualtrics_data.csv", row.names = FALSE)
```

# 2. Load the hand-coded interviews
```{r}
nq1 <- read.csv("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/FAS_coding_data_COMPLETE.csv",
                stringsAsFactors = FALSE)
nq2 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/Post_scan_debrief.xlsx", sheet = "Responses")
nq3 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/WASI_complete.xlsx")
nq4 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/4_17_MedHealth_Extraction.xlsx", sheet="Data")
nq5 <- read.csv("/Volumes/danl/ELFK/ELFK_Server/Questionnaires/archived_qualtrics_2018/CBCL_CLEANED/CBCL_scales_and_indiv_items_cleaned_MVT_12_2_2018.csv",
                stringsAsFactors = FALSE)
nq6 <- read.csv("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/saliva_time_date_long.csv",
                stringsAsFactors = FALSE)
nq7 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/Weight_from_MRI_completed_checked.xlsx")
nq8 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/KSADS_background_dx_COMPLETE_checked_BC_edited.xlsx") 
nq9<- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/LifeEvents_database_AW.xlsx", sheet="LifeEventsQuestionnaire")
nq10 <- readxl::read_excel("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/Scan_debriefing_parents.xlsx", sheet="Parents_debriefing")
nq11 <- readRDS("/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/cort_testos_crp_wide_biomarker.rds")
```

##data cleaning: replace "-8" in the medhealth questionnaire with NA
```{r}
#ALSO: Ensure the subject IDs are in the appropriate format
nq1 <- nq1 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq2 <- nq2 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq3 <- nq3 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq4 <- nq4 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq5 <- nq5 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq6 <- nq6 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq7 <- nq7 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq8 <- nq8 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq9 <- nq9 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
  #compute LEQ_MAX_IMPACT
nq9$LEQ_MAX_IMPACT<- apply(
  nq9[grep("IMPACT",names(nq9))], 1, function(x) max(x,na.rm = TRUE)) %>%
  replace(.,is.infinite(.),NA_integer_)
nq9$LEQ_MEAN_IMPACT <- apply(
    nq9[grep("IMPACT",names(nq9))], 1, function(x) mean(x,na.rm = TRUE)) %>%
    replace(.,is.nan(.),NA_integer_)
nq10 <- nq10 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))
nq11 <- nq11 %>% 
  mutate_at(1, function(x) as.vector(as.character(x))) %>%
  ELFK.identsubid("IDENT_SUBID") %>%
  rename_at(1, function(x) replace(x,1,"IDENT_SUBID"))

nq4[] <- lapply(nq4, function(x) replace(x, x == -8, NA))
#create master list of subject IDs
nq.master.id.list <- c()
for (i in 1:8) {
  nq.master.id.list <- c(nq.master.id.list,
                      unlist(getElement(
                        .GlobalEnv, paste("nq", i, sep = "")
                        )[, "IDENT_SUBID"]))
}
nq.master.id.list <- trimws(unique(nq.master.id.list))
#remove test/mock data that was left in the dataset
nq.master.id.list <- nq.master.id.list[
  which(as.numeric(sub("EL","",nq.master.id.list))<170)
  ]
#change the names of the child debrief variables (to distinguish w/ parent version)
nq2 <- nq2 %>%
  rename_at(-1,toupper) %>% 
  rename_at(-1, function(x) paste0("CHILD_",x))

nq10 <- nq10 %>%
  rename_at(-1,toupper) %>% 
  rename_at(-1, function(x) paste0("PARENT_",x))

#ignore warning messages
```

##convert nq6 to wide format (from long)
```{r}
d_wide <- data.frame("IDENT_SUBID" = unique(nq6$IDENT_SUBID),
                     "IN_LAB_1_DATE" = NA,
                     "IN_LAB_2_DATE" = NA,
                     "PRE_MRI_DATE" = NA,
                     "POST_MRI_DATE" = NA,
                     "IN_LAB_1_TIME" = NA,
                     "IN_LAB_2_TIME" = NA,
                     "PRE_MRI_TIME" = NA,
                     "POST_MRI_TIME" = NA)
#pull in the info conditional on values of "sample_type"
for (i in seq_along(d_wide$IDENT_SUBID)) {
  who <- d_wide$IDENT_SUBID[i]
  if (any(nq6[nq6$IDENT_SUBID == who, "sample_type"] == 1)) {
    d_wide[
      d_wide$IDENT_SUBID == who, c("IN_LAB_1_DATE","IN_LAB_1_TIME")
      ] <- nq6[
        nq6$IDENT_SUBID == who & nq6$sample_type == 1, 
        c("date_sample","time_sample_military")
        ]
  }
  if (any(nq6[nq6$IDENT_SUBID == who, "sample_type"] == 2)) {
    d_wide[
      d_wide$IDENT_SUBID == who, c("IN_LAB_2_DATE","IN_LAB_2_TIME")
      ] <- nq6[
        nq6$IDENT_SUBID == who & nq6$sample_type == 2, 
        c("date_sample","time_sample_military")
        ]
  }
  if (any(nq6[nq6$IDENT_SUBID == who, "sample_type"] == 3)) {
    d_wide[
      d_wide$IDENT_SUBID == who, c("PRE_MRI_DATE","PRE_MRI_TIME")
      ] <- nq6[
        nq6$IDENT_SUBID == who & nq6$sample_type == 3, 
        c("date_sample","time_sample_military")
        ]
  }
  if (any(nq6[nq6$IDENT_SUBID == who, "sample_type"] == 4)) {
    d_wide[
      d_wide$IDENT_SUBID == who, c("POST_MRI_DATE","POST_MRI_TIME")
      ] <- nq6[
        nq6$IDENT_SUBID == who & nq6$sample_type == 4, 
        c("date_sample","time_sample_military")
        ]
  }
}
#replace object 'nq6' with the new version
nq6 <- d_wide
```

##merge them all
```{r}
ndf.merge <- data.frame("IDENT_SUBID" = as.character(
  nq.master.id.list)) #start with the df of just IDENT_SUBID's
ndf.merge$IDENT_SUBID <- as.vector(as.character(ndf.merge$IDENT_SUBID))
for (i in 1:10) { #merge all the others into it
  ndf.merge <- merge(ndf.merge, getElement(
    .GlobalEnv, paste0("nq", i) #pull data frame from global environment
    ), by = "IDENT_SUBID", all = TRUE) #merge using "IDENT_SUBID"
}
```

##write out csv and rds files
```{r}
saveRDS(ndf.merge, "/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/R/interview data.rds")
#convert all to character for .csv write-out to increase compatibility
form.data <- ndf.merge
form.data[] <- lapply(form.data, as.character)
write.csv(form.data, "/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/csv/interview_data.csv", row.names = FALSE)
```

# 3. Read in the family codes
```{r}
demog <- read.csv("/Volumes/danl/ELFK/ELFK_Server/DATA_ENTRY_MASTER/Finalized_copies_to_be_merged/ELFK_Demo_11_14_2018.csv", stringsAsFactors = FALSE)
#rename desired variables
names(demog) <- names(demog) %>%
  replace(names(demog) == "Subject.ID","IDENT_SUBID") %>%
  replace(names(demog) == "Group..0.control..1.PI.", "GROUP") %>%
  replace(names(demog) == "Age", "BEHAV_AGE") %>%
  replace(names(demog) == "Behav.Date", "BEHAV_DATE") %>%
  replace(names(demog) == "MRI.Date", "MRI_DATE") %>%
  replace(names(demog) == "sex", "SEX") %>%
  replace(names(demog) == "mri.age", "MRI_AGE")
#retain desired variables
demog2 <- demog %>%
  select(IDENT_SUBID,GROUP,SEX,DOB,BEHAV_DATE,BEHAV_AGE,MRI_DATE,MRI_AGE,Family_code) %>%
  #compute binary GROUP var
  mutate(ADOPT_YN = ifelse(GROUP == 0, 0, 1))
```

# 4. Merge the Qualtrics data with the form data, then attach demographics w/ family code
```{r}
#(A) Merge the Qualtrics and form data
master <- merge(df.merge,ndf.merge,by = "IDENT_SUBID",all=FALSE)
#(B) Merge demographics + family code
master2 <- merge(master,demog2,by = "IDENT_SUBID",all=FALSE)
```

# 5. impute the data based on family code
```{r}
#subset data frame based on variables that we want to impute based upon fam code
df.parent_vars <- master2[,c(
  grep("IDENT_SUBID", names(master2)),
  grep("^AIOI", names(master2)),
  grep("^PARENT", names(master2)),
  grep("Family_code",names(master2)))]
#remove parent-specific date variables, since they will ultimately be deleted anyway
df.parent_vars<-df.parent_vars[,-grep("DATE",names(df.parent_vars))]

#obtain a list of every unique family code
duped.fam_code <- unique(
  df.parent_vars$Family_code[
    duplicated(df.parent_vars$Family_code)
    ]
  )
# instantiate function to fill a row based on criteria 
# that a row is related to another via Family_code, and is also currently missing data
fill <- function(column) {
  if (any(is.na(column))) {
    new <- replace(column, is.na(column), column[!is.na(column)][1])
    return(new)
  } else
    return(column)
}
#use function to fill in data for siblings
for (i in seq_along(duped.fam_code)) {
  dat <- df.parent_vars[df.parent_vars$Family_code == duped.fam_code[i],]
  dat[] <- lapply(dat, fill)
  df.parent_vars[df.parent_vars$Family_code == duped.fam_code[i],] <- dat
}
```
#substitute the corrected data back into the master data frame from which it was extracted
```{r}
master2[,names(df.parent_vars)] <- df.parent_vars
```
#Coalesce the duplicates that resulted in multiples of the CBCL variables
```{r}
a<-cbind(extr("\\.x$",names(master2)),extr("\\.y$",names(master2)))
b<-as.data.frame(
  matrix(
    apply(a, 1, function(x) {
      coalesce(master2[,x[1]],master2[,x[2]])
      }), ncol = nrow(a),
    dimnames = list(NULL,gsub("\\.x","",a[,1]))
    )
  )
```
#Insert them in place of the duplicated CBCL variables; reorder
```{r}
master3 <- cbind(
  master2[-c(grep("\\.x$",names(master2)), grep("\\.y$",names(master2)))], b
) %>% #put CBCL variables adjacent to one another
  select(IDENT_SUBID, starts_with("CBCL"), everything())
```

# 6. Write out the data entry master files
```{r}
saveRDS(master3, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/R/ELFK_Master_Data.rds")
```

# 7. Write out CSV and SPSS files
```{r}
write.csv(master3,"/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/csv/ELFK_Master_Data.csv", row.names = FALSE)
haven::write_sav(master3,"/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/04 Merged/SPSS/ELFK_Master_Data.sav")
```



