---
title: "Child DSM Cross Cutting tidying"
author: "Ian Douglas"
date: "3/14/2019"
output: html_document
---
#Load csv data
#Data exported from qualtrics on 3/13/19
```{r}
rm(list=ls()) #remove all objects in environment
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Children/DSM Cross Cutting raw.csv", stringsAsFactors = FALSE)
```

#Check the subject ID field for mock/test data
```{r}
#by location
head(df$Q1)
which(df$Q1=="")
#Conclusion:::No mock/test data entered at the beginning of the form
#No missing ID numbers
```

#Extract relevant variables
###Replace user-entered date with the Qualtrics timestamp
```{r}
df1 <- df[3:nrow(df),] %>% select(RecordedDate, starts_with("Q"),-Q4)
```

#Check for duplicates in the IDs
```{r}
test<-mutate(df1, 
             Q1 = as.integer(str_extract(df1$Q1,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q1)
#then define "dup"
dup <- which(duplicated(test$Q1))
dup
# integer(0)
#:::Conclusion: no duplicates entered or introduced in processing
```

#Standardize the IDs to ELFK format
```{r}
df2 <- df1 %>%
  # extract id NUMBERS only
  mutate(Q1 = as.integer(str_extract(df1$Q1, 
                                         pattern ="\\(?[0-9,.]+\\)?")))%>%
  # add prefix "EL00", "EL0", or "EL" as necessary; rename:
  mutate(IDENT_SUBID = paste0(ifelse(nchar(Q1)==1,"EL00",
                                ifelse(nchar(Q1)==2,"EL0",
                                       "EL")), Q1)) %>%
  select(RecordedDate, IDENT_SUBID, everything(),-Q1)
```

#Standardize the dates from character to numeric
####Exclude hours, minutes, and seconds
```{r}
df3 <- df2 %>% mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```

#Put the numeric variables in their appropriate data-type
```{r}
df4 <- df3 %>% mutate_at(3:ncol(df3), function(x) as.numeric(x))
```

#Attach the variable names
```{r}
var_names <- NULL
for (i in 1:23) {
  var_names[i] <- paste0("KSADS_DSM",i,"_C")
}
var.names <- c("KSADS_DSM_DATE_C","IDENT_SUBID",
               "KSADS_DSM_AGE_C","KSADS_DSM_GENDER_C",var_names)
names(df4) <- var.names
```

#For binary variables, recode "No" from 2 to 0
```{r}
df5 <- df4 %>% mutate_at(ncol(df4):(ncol(df4)-3), function(x) sub(2,0,x))
```

#For other numeric variables:
###Shift the scale from 0 to 3 (from 1 to 4)
```{r}
df6 <- df5 %>% mutate_at(5:(ncol(df4)-4), function(x) x-1)
```

#Fix the variable names
```{r}
var.names <- names(df6)
new.names <-c(
  sub("KSADS_", "", var.names[1]), 
  "IDENT_SUBID",  
  sub("KSADS_", "", var.names[3:4]),
  sub("KSADS_DSM", "DSM_", var.names[-1:-4])
  )
names(df6) <- new.names
```

Done!
##Write out tidy .Rds
```{r}
write_rds(df6,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/R/DSM_C_tidy.rds")
```
