---
title: "GHIQ tidying"
author: "Ian Douglas"
date: "4/17/2019"
output: html_document
---
#Load in the extracted data from qualtrics
```{r}
rm(list=ls())
library(tidyverse)
df <- read.csv("/Volumes/danl/ELFK/data_entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/Parent GHIQ raw.csv", stringsAsFactors = F)
```
#view the subject ID column to identify fake/mock data
```{r}
df$Q19[1:20]
```
#subject data begins on line 10
```{r}
df1 <- df[10:nrow(df),] %>% select(RecordedDate, starts_with("Q"))
```
#First correct the typo for participant "EL061"
```{r}
#leave the "p" so that we can later distinguish the child and parent response later.
df1$Q19[which(df1$Q19 == "elo6lp")] <- "EL061p"
```

#Search for duplicates
```{r}
#full list of duplicates
dupl1 <- id.search(df1, "Q19", "RecordedDate")
```
#make a list of all ids resulting in duplicate entry
```{r}
all.ids <- na.omit(
  c(as.vector(dupl1$Raw.entry.1), as.vector(dupl1$Raw.entry.2),
    as.vector(dupl1$Raw.entry.3), as.vector(dupl1$Raw.entry.4),
    as.vector(dupl1$Raw.entry.5))
)
child.dupl.ids <- all.ids[-grep("p", all.ids, ignore.case = T)]
parent.dupl.ids <- all.ids[grep("p", all.ids, ignore.case = T)]
```
#create dataframe consisting of child-generated duplicates
```{r}
child.dupl.df1 <- df1[df1$Q19 %in% child.dupl.ids,]
View(child.dupl.df1)
```
#create dataframe consisting of parent-generated duplicates
```{r}
parent.dupl.df1 <- df1[df1$Q19 %in% parent.dupl.ids,]
View(parent.dupl.df1)
```
#re-run the search to find further duplicates in each group
###First in child group
```{r}
reduced.search.child <- id.search(child.dupl.df1, "Q19","RecordedDate")
final.dupl.ids_c <- c(
  as.vector(reduced.search.child$Raw.entry.1),
  as.vector(reduced.search.child$Raw.entry.2),
  as.vector(reduced.search.child$Raw.entry.3)
  )
#look through the raw entries to manually determind which to keep.
duplicated.children<-child.dupl.df1[child.dupl.df1$Q19 %in% final.dupl.ids_c,]
View(duplicated.children)
```
###And in parent group
```{r}
reduced.search.parent <- id.search(parent.dupl.df1, "Q19","RecordedDate")
final.dupl.ids_p <-c(
  as.vector(reduced.search.parent$Raw.entry.1),
  as.vector(reduced.search.parent$Raw.entry.2),
  as.vector(reduced.search.parent$Raw.entry.3)
  )
#look through the raw entries to manually determind which to keep.
duplicated.parents<-parent.dupl.df1[parent.dupl.df1$Q19 %in% final.dupl.ids_p,]
View(duplicated.parents)
```
#Load in other data that has the IDs matched up with gender
```{r}
#csv
```


#collect cases that hadn't produced a duplicate and analyze if parent or child entered
```{r}
uniques<-c(apply(rbind(as.matrix(dupl1$Raw.entry.1,ncol =1),as.matrix(dupl1$Raw.entry.2,ncol =1),as.matrix(dupl1$Raw.entry.3,ncol =1),as.matrix(dupl1$Raw.entry.4,ncol =1),as.matrix(dupl1$Raw.entry.5,ncol =1)), 2, na.omit))
capture<-NULL
for (i in 1:length(df1$Q19)){
  if ((any(uniques == df1$Q19[i])) == F) {
    capture[i] <- df1$Q19[i]
  }
    
}
#capture now contains all the subject IDs that did not result in duplicates
#grab the original item from df1, assess if parent or child, and rbind it acordingly
unique.df1 <- df1[df1$Q19 %in% capture,]
uniq.parent.df1 <- unique.df1[grepl("p", unique.df1$Q19,ignore.case = T),]
uniq.child.df1 <- unique.df1[-grep("p", unique.df1$Q19,ignore.case = T),]
View(uniq.parent.df1)
View(uniq.child.df1)
```
#Now search for duplicates in the unique entries
```{r}
#1 of 2: uniq.parent.df1
id.search(uniq.parent.df1, "Q19", "RecordedDate")
#error message implies no duplicates, as expected, check!
```
```{r}
#2 of 2: uniq.parent.df1
id.search(uniq.child.df1, "Q19", "RecordedDate")
#error message implies no duplicates, as expected, check!
```


