---
title: "Grit tidying"
author: "Ian Douglas"
date: "3/14/2019"
output: html_document
---
#Tidying Script for the Child version of the Grit
##Load data
##Data exported from qualtrics 3/13/19
```{r}
#library(tidyverse)
df <- read.csv("/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Children/Grit Child raw.csv", stringsAsFactors = FALSE)
```

#Extract desired data from qualtrics output
####RETAIN THE TIMESTAMP [remove user-generated date]
```{r}
head(df$Q12)
# [1] "ID Number:"                    "{\"ImportId\":\"QID12_TEXT\"}"
# [3] ""                              "111"                          
# [5] "999"                           "EL001" 
# ::: Output suggests mock/test data ends at line 6
#
df1 <- df[6:nrow(df),] %>% select(RecordedDate, starts_with("Q"),-Q13)
```


#Check for errors within the subject ID column
```{r}
quantity.missing = function(x) {
  apply(x,2, function(x) length(which(x == "")))
}

where.na = function(x) {
  apply(x,2, function(x) sum(is.na(x)))
}

quantity.missing(df1)
where.na(df1)
```
```{r}
#:::Conclusion: there ar two missing in the subject ID column
#:::In addition, one entry contains all letters, and is fake data.
#Remove these cases
df2<-df1[-c(which(df1$Q12==""), all.letters(df1$Q12)),]
```


```{r}
#:::Proceed to search for other errors and duplicates
test<-mutate(df2, 
             Q12 = as.integer(str_extract(df2$Q12,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q12)
#then define "dup"
dup <- which(duplicated(test$Q12))
dup
#:::Output shows there are no duplicates. Proceed to format subject IDs
```

#Format subject IDs and dates to the standard ELFK format
```{r}
df3 <- df2 %>% ELFK.identsubid("Q12") %>% format.date("RecordedDate")
```

#Change the format of numeric variables
```{r}
df4 <- df3 %>% mutate_at(3:ncol(df3), function(x) as.numeric(x))
```

#Attach variable names
```{r}
var.names <- cbind("CHILD_GRIT_DATE_COMPLETE", "IDENT_SUBID","CHILD_GRIT_1", "CHILD_GRIT_2",
                   "CHILD_GRIT_3", "CHILD_GRIT_4", "CHILD_GRIT_5", "CHILD_GRIT_6", "CHILD_GRIT_7",
                   "CHILD_GRIT_8")
names(df4) <- var.names
```
#Flip positively-worded items around, rename all others
```{r}
#recode to accomplish the following:
#Agreement with positively-worded items reflects a higher score.
#Agreement with negatively-worded items reflects a lower score.

#reverse code the positively worded items to correct qualtrics coding error
df5 <- df4 %>% mutate_at(c(4,6,9,10),function(x) 6 - x)
#rename the "reverse-coded" items to indicate they are reverse-coded
#reverse-coding not necessary since qualtrics already flipped the output
names.adjusted <- c("GRIT_DATE_COMPLETE_C", "IDENT_SUBID","GRIT_1", "GRIT_2_C",
                   "GRIT_3", "GRIT_4_C", "GRIT_5", "GRIT_6", "GRIT_7_C",
                   "GRIT_8_C")
names(df5) <- names.adjusted
```

Done!
Write out the tidy .Rds, csv, sav, and dataframes.
```{r}
write_rds(df5,"/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/R/Grit_Child_tidy.Rds")
library(haven)
#convert all fields to character for csv and sav write-out
df6 <- as.data.frame(lapply(df5[,1:ncol(df5)], function(x) as.character(x)),
                     stringsAsFactors = F)
write.csv(df6, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/csv/Grit_Child_tidy.csv", row.names = FALSE)
write_sav(df6, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/SPSS/Grit_Child_tidy.sav")
```

