---
title: "IF tidying"
author: "Ian Douglas"
date: "4/15/2019"
output: html_document
---
#Load in raw IF data 
```{r}
(library(tidyverse))
rm(list=ls())
df.if <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/IF raw.csv", stringsAsFactors = FALSE)
```
#View the subject ID field
```{r}
df$Q1[1:20]
```
#mock/test data ends with row 9
```{r}
df1 <- df[10:nrow(df),] %>% select(RecordedDate, starts_with("Q"))
```
#Evaluate subject IDs
```{r}
#test to see if any subject IDs contain only letters
all.letters(vector = df1$Q1) 
#are there any missing data or NAs?
which(df1$Q1 == "")
which(is.na(df1$Q1))
#integer(0) indicates none
```
#Clean subject ID column
##Correct typo manually
```{r}
#per previous data management script "El0883" was a typo for subject EL083
df1$Q1 <- replace(df1$Q1, df1$Q1 == "El0883", "EL083")

```

##Search for duplicates
```{r}
id.search(df1, "Q1", "RecordedDate")
```
#Results show 4 duplicates, index cases to remove
```{r}
# 4 criteria were used to select which cases to remove:
#1.
#in addition to those found above, previous script indicates that manually entered
#data from paper version of this form will replace EL036 and EL037, so remove them too
#2.
#after analyzing responses, retain non-outlying response for "EL104" (they misread instructions)
#3. 
#For EL033 and EL006, retain the entry with more complete data.
#4.
#For the rest, the duplicate retained is the earlier entry.
rm <- c(ifelse(length(grep("36", df1$Q1)) == 1, grep("36", df1$Q1), NA),
        ifelse(length(grep("37", df1$Q1)) == 1, grep("37", df1$Q1), NA),
        which(df1$Q1 == "EL033" & df1$RecordedDate == "2015-12-21 12:02:15"
              | df1$Q1 == "EL006" & df1$RecordedDate == "2015-10-03 16:43:57"
              | df1$Q1 == "EL095" & df1$RecordedDate == "2018-04-30 13:45:14"
              | df1$Q1 == "EL104" & df1$RecordedDate == "2018-04-25 14:14:51"))
df2 <- df1[-rm,]
```
##standardize the subject ID to ELFK format
```{r}
df3 <- ELFK.identsubid(df2,"Q1")
```
#format the date
```{r}
df4 <- format.date(df3, "RecordedDate")
```
#convert numeric variables to appropriate data type
```{r}
df5 <- mutate_at(df4, 3:8,function(x) as.numeric(x))
```
#attach the variable names
```{r}
v.names <- c("IF_DATE_COMPLETE","IDENT_SUBID",
             "IF_1", "IF_2", "IF_3", "IF_4", "IF_5", "IF_6")
names(df5) <- v.names
```
#merge the hand-coded data from previous script
```{r}
merge.df <-as.data.frame(rbind(list('',"EL060", 1,1,5,8,4,5)
,list('',"EL056", 1,5,5,5, 5,5)
,list('',"EL053", 9,1,10,1,10,8)
,list('',"EL052", 3,6,7,3,7,6)
,list('',"EL051", 1,2,5,6,5,5)
,list('',"EL050", 3,4,7,3,6,5)
,list('',"EL049", 2,6,7,7,1,9) 
,list('',"EL048", 2,7,5,5,3,6)
,list('',"EL047", 2,8,4,8,1,4)
,list('',"EL046", 1,3,4,7,1,5)
,list('',"EL045", 1,1,3,8,1,3)
,list('',"EL044", 1,1,3,8,2,2)
,list('',"EL043", 1,10,7,4,1,1)
,list('',"EL042", 1,1,5,5,1,2)
,list('',"EL041", 2,2,5,4,4,4)
,list('',"EL040", 1,1,1,9,2,2)
,list('',"EL039", 7,5,9,1,9,8) 
,list('',"EL037", 1,10,5,2,8,8)  
,list('',"EL036", 1,10,5,3,5,7)
,list('',"EL035", 1,2,5,4,4,8)
,list('',"EL034", 2,6,6,4,4,8)
,list('',"EL025", 1,1,4,5,4,5)
,list('',"EL024", 2,2,7,2,4,6)
,list('',"EL023", 1,1,3,7,4,3)
,list('',"EL005", 1,5,1,9,1,1)
,list('',"EL004", 1,5,5,3,3,1)))
names(merge.df) <- v.names
overlapping.ids <- c(merge.df$IDENT_SUBID[which(merge.df$IDENT_SUBID %in% df5$IDENT_SUBID)])
df6 <- df5
for(i in 1:length(overlapping.ids)) {
  row.index.1 <- which(df5$IDENT_SUBID == overlapping.ids[[i]])
  row.index.2 <- which(merge.df$IDENT_SUBID == overlapping.ids[[i]])
  for (j in 1:6) {
    df6[row.index.1,j+2] <- merge.df[row.index.2,j+2]
  }
}
#make a list of the remaining participants to add that are not overlapping
uniq.merge <- merge.df[-c(which(merge.df$IDENT_SUBID %in% df5$IDENT_SUBID)),]
#convert classes before rbind-ing dfs
uniq.merge$IF_DATE_COMPLETE <-rep(NA, times = nrow(uniq.merge))
uniq.merge <- uniq.merge %>% mutate_at(3:8, function(x) as.numeric(x)) %>% 
  mutate_at(2, function(x) as.character(x)) %>%
  mutate_at(1, function(x) as.Date(x))
# > get.variable.classes(uniq.merge)
# classes
# character      Date   numeric 
#         1         1         6  ##Success!
```
#Merge the datasets
```{r}
df7 <- rbind(df6,uniq.merge)
```
#Done
#Write out the tidy data!
```{r}
write_rds(df7,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/IF_tidy.rds")
```


