---
title: "Motivation tidying"
author: "Ian Douglas"
date: "3/13/2019"
output: html_document
---
###Data exported from qualtrics 3/8/2019
#load data
```{r}
#library(tidyverse)
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Children/Motivation raw.csv", stringsAsFactors = FALSE)
```

#remove qualtrics artifacts, except for the timestamp!
```{r}
df1 <- df[3:nrow(df),] %>% select(RecordedDate, starts_with("Q"))
```
   
#check for missing data:
```{r}
quantity.missing = function(x) {
  apply(x,2, function(x) length(which(x == "")))
}

quantity.missing(df1)
```
   
#Now check for NAs:
```{r}
where.na = function(x) {
  apply(x,2, function(x) sum(is.na(x)))
}
where.na(df1)
```

##SKIP THIS CHUNK
###Conclusions from search implemented in next chunk
#Run the search algorithm for duplicated IDs...
```{r}
test<-mutate(df1, 
             Q1 = as.integer(str_extract(df1$Q1,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q1)
#then define "dup"
dup <- which(duplicated(test$Q1))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1==test$Q1[dup[i]]))),
                      df1$Q1[which(test$Q1==test$Q1[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1==test$Q1[dup[i]]))),
                      as.character(df1$RecordedDate[which(test$Q1==test$Q1[dup[i]])]))
}
#Create vector of raw times from which to pull times (since it was removed in df1)
time <- substr(df$RecordedDate, 12, nchar(as.character(df$RecordedDate)))
time <- time[-1:-2]
#create output matrix and run loop to collect the times:
times <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
for (i in 1:length(dup)) {
  times[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1==test$Q1[dup[i]]))),
                      time[which(test$Q1==test$Q1[dup[i]])])
}
#combine all matrices and order the columns to see associated info side by side.

search <- cbind(as.data.frame(duplicates),
                as.data.frame(dates),
                as.data.frame(times))[,c(4,9,14,5,10,15)]
search
```

#Delete the unwanted duplicate and mock/test data
```{r}
i <- as.integer(c(which(df1$Q1=="EL025" & df1$RecordedDate == "2015-12-06 11:39:49"), which(df1$Q1 =="999")))
df2 <- df1[-i,]
```

#Standardize subject IDs
```{r}
df3 <- df2 %>%
  # extract id NUMBERS only
  mutate(Q1 = as.integer(str_extract(df2$Q1, 
                                         pattern ="\\(?[0-9,.]+\\)?")))%>%
  # add prefix "EL00", "EL0", or "EL" as necessary; rename:
  mutate(IDENT_SUBID = paste0(ifelse(nchar(Q1)==1,"EL00",
                                ifelse(nchar(Q1)==2,"EL0",
                                       "EL")), Q1)) %>%
  select(RecordedDate, IDENT_SUBID, everything(),-Q1)
```

#Reformat the date field from character to "Date"
```{r}
df4 <- df3 %>% mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```

#Reformat the numeric variables to appropriate datatype
```{r}
df5 <- df4 %>% mutate_at(3:ncol(df4), function(x) as.numeric(x))
```

#Rename the variables appropriately
```{r}
var.names <- cbind("MOTIV_DATE_COMPLETE", "IDENT_SUBID", "MOTIVATION_1",
                   "MOTIVATION_2", "MOTIVATION_3", "MOTIVATION_4",
                   "MOTIVATION_5")
names(df5) <- var.names
```
#Qualtrics shifted the scale from 0-10 to 1-11, so subtract 1
```{r}
df6 <- df5 %>% mutate_at(3:7,function(x) x - 1)
```
#In addition, one mock subject ID is "312"
```{r}
removal <- grep("312",df6$IDENT_SUBID)
df7 <- df6[-removal,]
```


Done!
##Write out tidy .Rds, .csv and.sav
#This data does not need to be scaled;
##the variables are scores.
###No tidied data will be saved seperately.
#Write out finalized, scaled data.
```{r}
write_rds(df7,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/Motivation.rds")
#Convert to character before writing out .csv and .sav
library(haven)
df8<-as.data.frame(lapply(df7,as.character),stringsAsFactors=F)
write.csv(df8, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/csv/Motivation_final.csv", row.names = FALSE)
write_sav(df8, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/SPSS/Motivation_final.sav")
```

