---
title: "RADS tidying"
author: "Ian Douglas"
date: "5/15/2019"
output: html_document
---
#load raw data, extracted 5/15/2019
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/RADS raw.csv", stringsAsFactors = FALSE)
```

View subj ID column to identify fake data
```{r}
head(df$Q1) #delete the first two rows
```
#Extract desired info
```{r}
df1 <- df[-1:-2,] %>% select(RecordedDate, starts_with("Q"))
```
#look for duplicates in the subj ID field
```{r}
id.search(df1, "Q1", "RecordedDate")
```
Looks like there are some fake-date entries (with no digits), and subject 147 repeated their entry.
UPDATE: according to Michelle L's note, the second entry is the same parent, but refers to the sibling "EL146"; change the name.
```{r}
df1$Q1[
  which(df1$Q1 == "EL147" & df1$RecordedDate == "2018-06-07 13:38:25")
  ] <- "EL146"
#delete the two entries without digits
df2 <- df1[-which(grepl("[0-9]",df1$Q1) == FALSE),]
```
#Format the dates
```{r}
df3 <- format.date(df2,"RecordedDate")
```
#Standardize the subj ID
```{r}
df4 <- ELFK.identsubid(df3, "Q1")
```
#convert numeric variables to numeric class
```{r}
df5 <- df4 %>% 
  mutate_at(-c(grep("RecordedDate",names(df4)),
               grep("Q1", names(df4))),
            function(x) as.numeric(x))
```
(Cross-checking with qualtrics, qualtrics coded everything correctly); yes = 1, no = 0; num user-selected = output.
#Attach the variable names
```{r}
#attach the variable names
vnam <- c("RADS_DATE_COMPLETE","IDENT_SUBID", "RADS1", 
          "RADS2", "RADS3", "RADS4", "RADS5", "RADS6", 
          "RADS7", "RADS8", "RADS9", "RADS10","RADS11", 
          "RADS12", "RADS13", "RADS14", "RADS15", "RADS16",
          "RADS17", "RADS18", "RADS19", "RADS20","RADS21", 
          "RADS22", "RADS23", "RADS24", "RADS25", "RADS26")
names(df5) <- vnam
```
Done!
#Save the tidied data
```{r}
saveRDS(df5,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/R/RADS_tidy.rds")
```


