---
title: "RPQ tidying"
author: "Ian Douglas"
date: "5/15/2019"
output: html_document
---
#load raw data, extracted 5/15/2019
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(psych))
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/RPQ raw.csv", stringsAsFactors = FALSE)
```

View subj ID column to identify fake data
```{r}
head(df$Q1) #delete the first three rows
tail(df$Q1) #last row contains fake data
```
#Extract desired info
```{r}
df1 <- df[-c(1:2,nrow(df)),] %>% select(RecordedDate, starts_with("Q"))
```
#look for duplicates in the subj ID field
```{r}
id.search(df1, "Q1", "RecordedDate")
```
According to Michelle L's notes, retain only the 1 (of 3) entry of "EL145" that occurred imediately after the entry for the sibling EL144. 
```{r}
i <- c(which(df1$Q1 == "EL145" & df1$RecordedDate == "2018-06-12 17:40:26"),
        which(df1$Q1 == "EL145" & df1$RecordedDate == "2018-06-21 15:27:13"))
df2 <- df1[-i,]
```
#Format the dates
```{r}
df3 <- format.date(df2,"RecordedDate")
```
#Standardize the subj ID
```{r}
df4 <- ELFK.identsubid(df3, "Q1")
```
#convert numeric variables to numeric class
```{r}
df5 <- df4 %>% 
  mutate_at(-c(grep("RecordedDate",names(df4)),
               grep("Q1", names(df4))),
            function(x) as.numeric(x))
```
Cross-checking with qualtrics, qualtrics reverse coded everything, and shifted the range from 1 to 4, as opposed to 0 to 3.
```{r}
#require(psych)
df6 <- data.frame(
  df5[1:2],
  reverse.code(keys = rep(-1, times = (ncol(df5)-2)),
               items = df5[-1:-2]) - 1) #SUBTRACT 1 also
```

#Attach the variable names
```{r}
#attach the variable names
vnam <- c("RPQ_DATE_COMPLETE","IDENT_SUBID", 
          "RPQ1", "RPQ2","RPQ3","RPQ4","RPQ5",
          "RPQ6","RPQ7","RPQ8","RPQ9")
names(df6) <- vnam
```
Done!
#Save the tidied data
```{r}
saveRDS(df6,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/R/RPQ_tidy.rds")
```
