---
title: "BDI tidying"
author: "Ian Douglas"
date: "6/3/2019"
output: html_document
---
#load in raw data
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/BDI 1A raw.csv", stringsAsFactors = FALSE)
```
#View subject ID column
```{r}
df$Q24[1:10] #real data starts on row 9
tail(df$Q24, 10)
```
#Extract desird data
```{r}
df1 <- df[-1:-8,] %>% select(RecordedDate, starts_with("Q"))
```
#Check for duplicates in the subject ID column
```{r}
id.search(df1, "Q24", "RecordedDate")
```
1. correct typo (for EL061) that ostensibly created a duplicate, but was not one.
```{r}
df1$Q24 <- replace(df1$Q24, df1$Q24=="el06lp", "EL061")
```
2. correct typo (for EL081) that ostensibly created a duplicate, but was not one.
```{r}
df1$Q24 <- replace(df1$Q24, df1$Q24=="El08lp", "EL081")
```
3. Retain the first entry (from 2016 as opposed to 2017) of EL071
```{r}
index1 <- which(
  df1$Q24 == "EL071P" & df1$RecordedDate == "2017-02-24 14:01:42"
  )
```
4. Delete the first entry of EL097 because it contains all missing data
```{r}
index2 <- which(
  df1$Q24 == "EL097" & df1$RecordedDate == "2017-05-31 12:10:56"
  )
```
5. Retain the first entry of EL079 completed on the date of lab visit
```{r}
index3 <- which(
  df1$Q24 == "EL079P" & df1$RecordedDate == "2016-10-16 10:59:20"
)
```
6. Retain the first entry of EL140
```{r}
index4 <- which(
  df1$Q24 == "el140" & df1$RecordedDate == "2018-04-10 13:42:33"
  )
```
#Delete unwanted entries
```{r}
to.delete <- c(index1, index2, index3, index4)
df2 <- df1[-to.delete,]
```
#Check that there are no more duplicates:
```{r}
id.search(df2, "Q24", "RecordedDate") #Error should read "There are no duplicates"
```
#format the id field and date
```{r}
df3 <- df2 %>% ELFK.identsubid("Q24") %>% format.date("RecordedDate")
```
#correct the datatypes
```{r}
df4 <- df3 %>%
  mutate_at(3:ncol(.), as.numeric)
```
#Shift the data so that responses span 0 to 3, not 1 to 4
```{r}
df5 <- df4 %>%
  mutate_at(3:ncol(.), function(x) (x-1))
```
#Attach the names
```{r}
item.names <- NULL
for (i in 1:(ncol(df5)-2)) {
  item.names[i] <- paste0("PARENT_BDI1A_", i, collapse = "")
}
vnam <- c("PARENT_BDI1_DATE", "IDENT_SUBID", item.names)
names(df5) <- vnam
```
#merge in the PACCT participants
```{r}
df.pacct <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/PACCT/pacct.csv", stringsAsFactors = FALSE)
```
#retain bdi data only
```{r}
df1.pacct <- df.pacct %>%
  select(IDENT_SUBID, starts_with("BDI_"))
```
#extract the three participants for whom this data is actually completed
```{r}
#also, delete the columns containing variables created for another study
df2.pacct <- df1.pacct[
  df1.pacct$IDENT_SUBID %in% c("EL144","EL145","EL149"), -grep(".J", names(df1.pacct))
  ]
```
#fix the names
```{r}
item.names.pacct <- NULL
num <- c(1:8,10:21) #exclude 9
for (i in 1:(ncol(df2.pacct)-1)) {
  item.names.pacct[i] <- paste0("PARENT_BDI2_", num[i], collapse = "")
}
vnam.pacct <- c("IDENT_SUBID", item.names.pacct)
names(df2.pacct) <- vnam.pacct
```

#merge the dataframes
```{r}
#(drop date from BDI-1A data frame)
bdi.1a <- data.frame(df5[-1], matrix(rep(NA, times = nrow(df5)*(ncol(df2.pacct)-1)),
                                     ncol = (ncol(df2.pacct)-1),
                                     dimnames = list(NULL, names(df2.pacct[-1]))))
bdi.2 <- data.frame(df2.pacct[1],
                    matrix(rep(NA, times = nrow(df2.pacct)*(ncol(df5)-2)),
                           ncol = (ncol(df5)-2),
                           dimnames = list(NULL, names(df5)[-1:-2])),
                    df2.pacct[-1])
#merge
bdi <- rbind(bdi.1a,bdi.2)
```
#On final review, it turns out EL144 and EL149 filled out both versions, so combine their data
```{r}
for (i in 1:(ncol(bdi)-1)) {
  bdi[grep("EL149",bdi$IDENT_SUBID)[1],i+1] <- ifelse(
    is.na(bdi[grep("EL149",bdi$IDENT_SUBID)[1],i+1]),
    bdi[grep("EL149",bdi$IDENT_SUBID)[2],i+1],
    bdi[grep("EL149",bdi$IDENT_SUBID)[1],i+1]
  )
}
for (i in 1:(ncol(bdi)-1)) {
  bdi[grep("EL144",bdi$IDENT_SUBID)[1],i+1] <- ifelse(
    is.na(bdi[grep("EL144",bdi$IDENT_SUBID)[1],i+1]),
    bdi[grep("EL144",bdi$IDENT_SUBID)[2],i+1],
    bdi[grep("EL144",bdi$IDENT_SUBID)[1],i+1]
  )
}
#Remove the duplicate
bdi.final <- bdi[!duplicated(bdi$IDENT_SUBID),]
```



#Done!
Write out tidy data
```{r}
saveRDS(bdi.final,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/bdi_tidy.rds")
```


