---
title: "CQ tidying"
author: "Ian Douglas"
date: "4/15/2019"
output: html_document
---
#Load in raw CQ data 
```{r}
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/CQ raw.csv", stringsAsFactors = FALSE)
```

#Filter unwanted data in the subject ID field:
```{r}
#blank rows:
rm <-which(df$Q4 == "")
#entires that contain no numbers
rm1 <- which(grepl("^[A-Za-z]+$", df$Q4, perl = T)) #usually say "test"
#remove these fields, along with the headers in rows 1 and 2
df1 <- df[-c(1,2,rm,rm1),]
```

#select variables we want to retain
```{r}
df2 <- df1 %>% select(RecordedDate, starts_with("Q"))
```

#check to see if there are a lot of NA or missing in each column
```{r}
quantity.missing(df2)
quantity.zero(df2)
where.na(df2)
```
Columns "Q4...Topics" and "Q8..Topics" are extraneous; delete them
```{r}
df3 <- df2[,-c((ncol(df2)-1):ncol(df2))]
```
#search within the subject ID field for duplicates
```{r}
digits<-mutate(df3, 
             Q4 = as.integer(str_extract(df3$Q4,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q4)
#then define "dup"
dup <- which(duplicated(digits$Q4))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q4==digits$Q4[dup[i]]))),
                      df3$Q4[which(digits$Q4==digits$Q4[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup))), 
                ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q4==digits$Q4[dup[i]]))),
                 as.character(df3$RecordedDate[which(digits$Q4==digits$Q4[dup[i]])]))
}

#combine the matrices and order the columns to see associated info side by side.

search <- cbind(as.data.frame(duplicates),
                as.data.frame(dates))[,c(4,9,5,10)]
names(search) <- c("raw entry #1", "timestamp1","raw entry #2","timestamp2")
search
```
#determine if NAs were creeated within the subject ID column
```{r}
#index them to remove them
nas <- which(is.na(digits$Q4))
#now view the search matrix
search
```

#This is consisten with two duplicated NAs. In addition there are two real duplicates
```{r}
#index the cases to keep based on data completeness
rbind(df3[df3$Q4=="EL095",],df3[df3$Q4=="EL036",])
#for EL095 we should remove the 2017-3-21 obs, and Sept.2018 for EL036
i.rm <- c(which(df3$Q4 == "EL095" & df3$RecordedDate == "2017-03-21 09:48:58"),
          which(df3$Q4 == "EL036" & df3$RecordedDate == "2018-09-10 11:12:31"))
#Check to see if any mock data is still in the list of subject IDs based on numeric size
head(sort(digits$Q4,decreasing=T))
i.rm2 <- which(digits$Q4 == 999) #it is rwo 34
df4 <- df3[-c(i.rm,nas,i.rm2),]
```
#Standardize the subject ID column
```{r}
df5 <- ELFK.identsubid(df4, "Q4")
```
#merge in the one observation of EL143 from the same-sex parent form
```{r}
df143 <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/CQ same_sex raw.csv", stringsAsFactors = FALSE)
```
#Filter the desired columns
```{r}
df143.1 <- df143[-1:-2,] %>% select(RecordedDate, starts_with("Q")) #no extraneous column
```
#Set the names before merge the dataframes
```{r}
v.names <- c("CQ_DATE_COMPLETE","IDENT_SUBID","CQ1","CQ2","CQ3")
names(df143.1) <- v.names
names(df5) <- v.names
```
#merge the datasets
```{r}
df6 <- rbind(df5,df143.1)
```
#format the date column
```{r}
df7 <- df6 %>% 
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```
#recode one answer for the same-sex couple
```{r}
#EL143 answerd "Both parents" on their unique Qualtrics form, so adapt the output to the same code as "Both parents" for the original Qualtrics form that the rest of the subjects answerd:
df7[df7$IDENT_SUBID == "EL143",]$CQ2 <- .5
```
#Finally, convert numeric variables to data type numeric
```{r}
df8 <- df7 %>% mutate_at(3:5, as.numeric)
```
#manually add in the data that was recovered by previous data manager, Michelle L.
```{r}
#copying and pasting from her script; code each participant as follows:
missing.data<- matrix(c("1","1","1","0","1","1","0.5",
                        "Not sure","0","0.5","1","0","0.5","1",
                        "1","1","1","1","1","1","1","0.5","1","0","1",
                        "1","1","1","1","1","0.5","0","0","0.5","1",
                        "1","1","1","1","1","1","1","1","1",
                        "1","1","1","1","1","1","1","1","0.5","1","1",
                      "1","1","1","1","1","0.5","0.5","0.5","1","0.5",
                      "0.5","0.5","1","1","0.5","1","1","0.5","0","0",
                      "0.5","1","0","1","1","1","1","1","1","",
                      "","","","","","","",""), ncol = 3, byrow = T)
#convert from character to numeric, produce NAs for blankas as well
data.1 <- apply(missing.data, 2, as.numeric)
#merge the data in to the existing dataframe
#NOTE, the data is in the same order already as the missing cases from df8
df8$CQ1 <- c(data.1[1:31,1],df8$CQ1[32:nrow(df8)])
df8$CQ2 <- c(data.1[1:31,2],df8$CQ2[32:nrow(df8)])
df8$CQ3 <- c(data.1[1:31,3],df8$CQ3[32:nrow(df8)])
```

#No scoring necessary!
#Write out tidy and finalized data!
```{r}
write_rds(df8,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/03 Scored/R/CQ final.rds")
```

