---
title: "CRPR tidying"
author: "Ian Douglas"
date: "4/15/2019"
output: html_document
---
#Load in raw CRPR data 
```{r}
(library(tidyverse))
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/CRPR raw.csv", stringsAsFactors = FALSE)
```
#View the subject ID field
```{r}
df$Q1_1[1:20]
```
#mock/test data ends with row 8
```{r}
df1 <- df[9:nrow(df),] %>% select(RecordedDate, starts_with("Q"))
```
#Evaluate subject IDs
```{r}
#test to see if any subject IDs contain only letters
all.letters(vector = df1$Q1_1) 
#are there any missing data or NAs?
which(df1$Q1_1 == "")
which(is.na(df1$Q1_1))
#integer(0) indicates none
```
#Clean subject ID column
###according to previous data management script:
```{r}
#Make EL086P – first entry  – EL087. Leave second entry as EL086.
df1$Q1_1[df1$Q1_1 == "el086p"] <- "EL087" 
```
###As usual, EL061 typo'd their subject ID
```{r}
#re-enter EL061
df1$Q1_1[df1$Q1_1 == "elo6lp"] <- "EL061"
```

##Search for duplicates
```{r}
id.search(df1, "Q1_1", "RecordedDate")
```
##From results of search:
```{r}
#“EL041P” is actually EL042. then delete “EL042” as it is a true duplicate
#for cases where the duplicate entry is entered far after the original, delete the more recent
df1$Q1_1 <- replace(df1$Q1_1, df1$Q1_1 == "EL041P", "EL042")
removals <- c(which(
  df1$Q1_1 == "EL042" & df1$RecordedDate == "2018-05-22 07:17:17" |
    df1$Q1_1 == "EL127" & df1$RecordedDate == "2018-01-05 13:57:54" |
    df1$Q1_1 == "ELO96P"))
df2 <- df1[-removals,]
```
#convert data to numeric
```{r}
df2[-1:-3] <- lapply(df2[-1:-3], as.numeric)
```

#split the data frames to deal with cases that were creating duplicates
```{r}
df.deduped <- df2[!df2$Q1_1 %in% c(id.search(df2,"Q1_1","RecordedDate")$Raw.entry.1,id.search(df2,"Q1_1","RecordedDate")$Raw.entry.2),]
df.duped<-df2[df2$Q1_1 %in% c(id.search(df2,"Q1_1","RecordedDate")$Raw.entry.1,id.search(df2,"Q1_1","RecordedDate")$Raw.entry.2),]
#make the averages per family
f1.avg <- apply(df.duped[1:2,4:43], 2, mean)
f2.avg <- apply(df.duped[3:4,4:43], 2, mean)
f3.avg <- apply(df.duped[5:6,4:43], 2, mean)
f4.avg <- apply(df.duped[7:8,4:43], 2, mean)
f5.avg <- apply(df.duped[9:10,4:43], 2, mean)


#make rows for each sibling in each family.
df.duped.2 <- rbind(df.duped[1,],df.duped[1,],df.duped[1,],df.duped[1,],
                    df.duped[3,],df.duped[3,],
                    df.duped[6,],df.duped[6,],
                    df.duped[7,],df.duped[7,],df.duped[7,],df.duped[7,],df.duped[7,],
                    df.duped[9,],df.duped[9,])
df.duped.2[1:4,4:43] <- f1.avg
df.duped.2[5:6,4:43] <- f2.avg
df.duped.2[7:8,4:43] <- f3.avg
df.duped.2[9:13,4:43] <- f4.avg
df.duped.2[14:15,4:43] <- f5.avg

#correct the subject ID field
df.duped.2$Q1_1 <- c("EL002","EL003","EL004","EL005",
                     "EL019","EL020",
                     "EL036","EL037",
                     "EL081","EL082","EL083","EL084","EL085",
                     "EL086","EL087")
```
#Bind the data frames back together
```{r}
df3 <- rbind(df.deduped,df.duped.2)
```

##One parent filled out the form on behalf of both children
```{r}
# df3$Q1_1[grep("and", df3$Q1_1)]
# [1] "EL104 and EL105"
### Split this entry into two, duplicate the responses
df4 <- rbind(df3, df3[grep("and", df3$Q1_1),])
df4$Q1_1[grep("and", df4$Q1_1)] <- c("EL104","EL105")
```

##With subject IDs either correct or flagged, process IDs:
```{r}
df5 <- ELFK.identsubid(df4, "Q1_1")
#rename
names(df5) <- replace(
  names(df5), names(df5) == "Q1_1", "IDENT_SUBID"
  )
```

#Format the dates
```{r}
df6 <- format.date(df5, "RecordedDate")
#also remove the user-entered date
df6 <- df6[,-grep("Q1_2",names(df6))]
```

#attach the variable names
```{r}
v.names <- c("CRPR_DATE_COMPLETE","IDENT_SUBID", "CRPR_1",
                 "CRPR_2", "CRPR_3", "CRPR_4", "CRPR_5", 
                 "CRPR_6", "CRPR_7", "CRPR_8",
                 "CRPR_9", "CRPR_10", "CRPR_11", "CRPR_12",
                 "CRPR_13", "CRPR_14", "CRPR_15", "CRPR_16",
                 "CRPR_17","CRPR_18", "CRPR_19", "CRPR_20",
                 "CRPR_21", "CRPR_22", "CRPR_23", "CRPR_24",
                 "CRPR_25", "CRPR_26","CRPR_27", "CRPR_28",
                 "CRPR_29", "CRPR_30", "CRPR_31", "CRPR_32",
                 "CRPR_33", "CRPR_34", "CRPR_35",
                 "CRPR_36", "CRPR_37", "CRPR_38", 
                 "CRPR_39", "CRPR_40")
names(df6) <- v.names
```

#Done
#Write out the tidy data!
```{r}
write_rds(df6,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/CRPR_tidy.rds")
```


