---
title: "Untitled"
author: "Ian Douglas"
date: "3/29/2019"
output: html_document
---
#load in data and required packages
```{r}
rm(list=ls())
library(tidyverse)
df <- read.csv("/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/Grit Parent raw.csv", stringsAsFactors = FALSE)
```
#Visualize the id column to search for mock/test data
```{r}
df$Q17[1:20]
#Conclusion: real data begins on line 10
```
#extract desired rows and columns
```{r}
#note, leave out the user-generated date field
df1 <- df[-1:-9,] %>% select(RecordedDate, starts_with("Q"), -Q18)
```
#confirm no subject IDs were left blank or NA
```{r}
quantity.missing = function(x) {
  apply(x,2, function(x) length(which(x == "")))
}

where.na = function(x) {
  apply(x,2, function(x) sum(is.na(x)))
}

quantity.missing(df1)[2]
where.na(df1)[2]
```
#confirm that each subject ID entry contains a numeric digit
```{r}
digits <-mutate(df1, 
             Q17 = as.integer(str_extract(df1$Q17,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q17)
#The number of rows of "digits" should be equal to the raw data
length(digits$Q17) == nrow(df1)
#The values in digits$Q17 should all be numeric, none should be zero, none should be NA
quantity.missing(digits) #output should read 0
where.na(digits) #output should read 0
apply(digits,2, function(x) length(which(x == 0))) #output should read 0
```
#Lastly search for duplicates
```{r}
digits<-mutate(df1, 
             Q17 = as.integer(str_extract(df1$Q17,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q17)
#then define "dup"
dup <- which(duplicated(digits$Q17))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q17==digits$Q17[dup[i]]))),
                      df1$Q17[which(digits$Q17==digits$Q17[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup))), 
                ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q17==digits$Q17[dup[i]]))),
                 as.character(df1$RecordedDate[which(digits$Q17==digits$Q17[dup[i]])]))
}

#combine the matrices and order the columns to see associated info side by side.

search <- cbind(as.data.frame(duplicates),
                as.data.frame(dates))[,c(4,9,5,10)]
names(search) <- c("raw entry #1", "timestamp1","raw entry #2","timestamp2")
search
```
###Conclusion: "EL061" entered an "l" instead of a "1"
###Manually correct this typo
```{r}
df1$Q17 <- replace(df1$Q17, grep("el06lp", df1$Q17), "EL061")
```
#Now standardize the subject IDs
```{r}
df2 <- ELFK.identsubid(df1, "Q17")
```
#Format data field
```{r}
df3 <- df2 %>% 
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```
#convert all numeric variables to correct data type
```{r}
#numeric variables include all except the date and subject id
df4 <- mutate_at(df3, -1:-2, as.numeric)
```

#attach the correct variable names
```{r}
v.names<-c("PARENT_GRIT_DATE_COMPLETE", "IDENT_SUBID", "PARENT_GRIT_1",
           "PARENT_GRIT_2","PARENT_GRIT_3","PARENT_GRIT_4","PARENT_GRIT_5","PARENT_GRIT_6","PARENT_GRIT_7",
           "PARENT_GRIT_8","PARENT_GRIT_9","PARENT_GRIT_10","PARENT_GRIT_11","PARENT_GRIT_12")
names(df4) <- v.names
```
#Flip positively-worded items around, rename all others
```{r}
#reverse code the positively worded items to correct qualtrics coding error
df5 <- df4 %>% mutate_at(c(3,6,8,11,12,14),function(x) 6 - x)
#rename the "reverse-coded" items to indicate they are reverse-coded
#reverse-coding not necessary since qualtrics already flipped the output
names.adjusted <- c("PARENT_GRIT_DATE_COMPLETE", "IDENT_SUBID", "PARENT_GRIT_1",
           "PARENT_GRIT_2","PARENT_GRIT_3","PARENT_GRIT_4","PARENT_GRIT_5","PARENT_GRIT_6","PARENT_GRIT_7",
           "PARENT_GRIT_8","PARENT_GRIT_9","PARENT_GRIT_10","PARENT_GRIT_11","PARENT_GRIT_12")
names(df5) <- names.adjusted
```
#write out and save the tidy data
```{r}
write_rds(df5,"/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/Grit_Parent_tidy.Rds")
library(haven)
#convert all fields to character for csv and sav write-out
df6 <- as.data.frame(lapply(df5[,1:ncol(df5)], function(x) as.character(x)),
                     stringsAsFactors = F)
write.csv(df6, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/csv/Grit_Parent_tidy.csv", row.names = FALSE)
write_sav(df6, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/SPSS/Grit_Parent_tidy.sav")
```


