---
title: "International Adoption Inventory tidying"
author: "Ian Douglas"
date: "3/25/2019"
output: html_document
---

```{r}
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/PI/IAI raw.csv", stringsAsFactors = FALSE)
```

#extract desired data
```{r}
#Calling head(df$Q1) suggests that the "real" data starts on row 4
df1 <- df[4:nrow(df),] %>% select(RecordedDate,starts_with("Q"))
```
#search for erroneous entries in the subjet ID column
```{r}
quantity.missing = function(x) {
  apply(x,2, function(x) length(which(x == "")))
}

where.na = function(x) {
  apply(x,2, function(x) sum(is.na(x)))
}

quantity.missing(df1)[2]
where.na(df1)[2]
#Conclusion: no missing or NA in the subject ID column
```
```{r}
#RUN THE FULL SEARCH ALGORITHM
test<-mutate(df1, 
             Q1 = as.integer(str_extract(df1$Q1,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q1)
#then define "dup"
dup <- which(duplicated(test$Q1))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1==test$Q1[dup[i]]))),
                      df1$Q1[which(test$Q1==test$Q1[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup))), 
                ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1==test$Q1[dup[i]]))),
                 as.character(df1$RecordedDate[which(test$Q1==test$Q1[dup[i]])]))
}

#combine the matrices and order the columns to see associated info side by side.

search <- cbind(as.data.frame(duplicates),
                as.data.frame(dates))[,c(4,9,5,10)]
names(search) <- c("raw entry #1", "timestamp1","raw entry #2","timestamp2")
search
```
#Conclusion: there are two duplicates, one each for clients EL104 and EL105
#As per discussion with Michelle V. and Bridget C., remove newer entry
```{r}
#index the rows to remove
i <- c(which(df1$Q1=="EL104" & df1$RecordedDate == "2018-06-13 17:58:57"),
       which(df1$Q1=="EL105" & df1$RecordedDate == "2018-06-13 18:07:06"))
#remove them
df2 <- df1[-i,]
```
#Standardize the subject ID field
```{r}
df3 <- ELFK.identsubid(df2,"Q1")
```
#format the dates (remove hours, minutes, and seconds)
```{r}
df4 <- df3 %>% 
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```
#attach the variable names
```{r}
var.names <- cbind("IAI_DATE_COMPLETE","IDENT_SUBID", "IAI_1A_COUNTRYADOPT",
                   "IAI_1B_CITYBORN", "IAI_2_CITYSIZE","IAI_3_AGEORPH",
                   "IAI_4_HOWORPH",
                   "IAI_5A_SEEORPH","IAI_5B_QUALBUILD",
                   "IAI_5C_CLEANFAC", "IAI_5D_QUANTCAREG", "IAI_5E_QUALCAREG",
                   "IAI_6A_SPECBOND", "IAI_6B_EXPLAN", "IAI_7_AGEADOPT",
                   "IAI_8_HEALTHADOPT", "IAI_9A_HEALTHCONDADOPT",
                   "IAI_9B_EXPLAN", "IAI_10A_HEALTHCONDLATER", 
                   "IAI_10B_EXPLAN", "IAI_11_REACTMEET", 
                   "IAI_12_MONTHADJUST", "IAI_13_CHALLADOPTINT", 
                   "IAI_14A_DEVADVANCE", "IAI_14B_EXPLAN", "IAI_15A_DEVSTRUG",
                   "IAI_15B_EXPLAN", "IAI_16_REWADOPT", "IAI_17_AREACHILDEXCEL",
                   "IAI_18_AREACHILDSTRUG", "IAI_19B_EXPLAN")

names(df4) <- var.names
#add the variable that we have to create
df4$IAI_19A_OTHERINFO <- ifelse(df4$IAI_19B_EXPLAN == "", 0L, 1L)
#change the order of the last two variables now
df4 <- df4[,c(1:(ncol(df4)-2),ncol(df4),(ncol(df4)-1))]
```

```{r}
#recode the country names so that there is one format per county
df4$IAI_1A_COUNTRYADOPT <- ifelse(df4$IAI_1A_COUNTRYADOPT=="USA" | df4$IAI_1A_COUNTRYADOPT=="US","United States",df4$IAI_1A_COUNTRYADOPT)
```
#code orphanage age question
```{r}
#interpret and recode the text according to the data entry manual
ageorph<-c(1L,NA_integer_,0L,0L,0L,2L,0L,1L,0L,0L, 0L,1L,0L,
            0L,2L,0L,4L,3L,1L, 3L,4L,3L,NA_integer_,0L,6L,9L,2L,1L,NA_integer_,
            4L,1L,9L,1L,2L,2L,1L,NA_integer_,0L,6L,4L,1L,0L,2L,1L,6L)
df5 <- df4 %>% mutate_at(which(names(df4)=="IAI_3_AGEORPH"),function(x) replace(x,1:45,ageorph))
```
#change desired variables to numeric from type character
```{r}
df5[c(5,6,8,9,10,11,12,13,16,17,19,21,24,26)]<-lapply(df5[c(5,6,8,9,10,11,12,13,16,17,19,21,24,26)],as.numeric)
```
#recode variables that were miscoded by qualtrics' output
```{r}
#The following variables have the following system:
#1 exported from qualtrics as "Yes", but "No" became 2 [fix "No" to 0]
i <- c(grep("IAI_5A_SEEORPH",names(df5)),
       grep("IAI_6A_SPECBOND",names(df5)),
       grep("IAI_9A_HEALTHCONDADOPT",names(df5)),
       grep("IAI_10A_HEALTHCONDLATER",names(df5)),
       grep("IAI_14A_DEVADVANCE",names(df5)),
       grep("IAI_15A_DEVSTRUG",names(df5)))
df5 <- df5 %>% mutate_at(i, function(x) replace(x,grep(2,x),0))
```
#code adoption age to numeric
```{r}
#interpret and recode the text according to the data entry manual
ageadopt<-c(10,24,10.5,9,14,8.5,10,11,10,10.5,10.5,10,9,11,4,15,
            22,26,15,42,72,90,6,24,30,36,20,48,.5,9,5,18.5,24,22,
            7.25,11,6,9,12,30,1.5,2,2,7,25)
df6 <- df5 %>% mutate_at(which(names(df5)=="IAI_7_AGEADOPT"),function(x) replace(x,1:nrow(df5),ageadopt))
#change datatype ot numeric
#df6 <- df5
df6[which(names(df6)=="IAI_7_AGEADOPT")] <- lapply(df6[which(names(df6)=="IAI_7_AGEADOPT")],as.numeric)
```
#code adjustment time variable to numeric
```{r}
#interpret and recode the text according to the data entry manual
timeadj<-c(9, 1, 1, 0, 2, 1, 2, 10, 0, 1,
           1, 2, 1, 3, 0, 5, 3, 0, 3, 3,
           5, 9, 0, 10, 3, 0, 1, 9, 0, 1,
           9, 1, 1, 4, 10, 4, 3, 0, 0, 9,
           1, 2, 2, 0, 1)
df6$IAI_12_MONTHADJUST <- timeadj 
```
#NOTE: merge in pacct participants in the "scoring" script
###Since pacct participants will only have partial data.

#Write out tidy data! 
```{r}
write_rds(df6,"/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/R/IAI_tidy.Rds")
library(haven)
#convert all fields to character for csv and sav write-out
df7 <- as.data.frame(lapply(df6[,1:ncol(df6)], function(x) as.character(x)),
                     stringsAsFactors = F)
write.csv(df7, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/csv/IAI_tidy.csv", row.names = FALSE)
write_sav(df7, "/Volumes/danl/ELFK/ELFK_server/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/PI/SPSS/IAI_tidy.sav")
```

