---
title: "SS tidying"
author: "Ian Douglas"
date: "3/8/2019"
output: html_document
---
###Data exported from qualtrics 3/8/2019
#load data
```{r}
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Children/Security Scale raw.csv")
```

#remove qualtrics artifacts, except for the timestamp!
```{r}
#supplant user-generated date entry with timestamp
df1 <- df[3:nrow(df),] %>% select(RecordedDate, starts_with("Q"),-Q1_2)
```
   
   
#check for missing data:
```{r}
# quantity.missing = function(x) {
#   apply(x,2, function(x) length(which(x == "")))
# }

quantity.missing(df1)
```
   
#Now check for NAs:
```{r}
# where.na = function(x) {
#   apply(x,2, function(x) sum(is.na(x)))
# }
where.na(df1)
```
   
#No missing or NA data found in subject ID column, proceed in creating ELFK IDs:
```{r}
#Tidy subject ID raw data:

#run the following algorithm to search for duplicates in subject ID column
df1[,which(names(df1)=="Q1_1")] <- as.character(df1$Q1_1)
test<-mutate(df1, 
             Q1_1 = as.integer(str_extract(df1$Q1_1,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q1_1)
#Check that the extracted digits are numbers greater than zero, no NAs:
#How many erroneously entered 0:
sum(test==0,na.rm=T) #no subject IDs contained only the number zero.

#How many contained no numbers (and became NA through above extraction):
where.na(test) # results show us one such case.

##SINCE above test for NA is greater than zero, obtain row index and raw data:
c(which(is.na(test)==TRUE), df1$Q1_1[which(is.na(test)==TRUE)])
# "fgh" refers to mock/test data, so delete that row, and then recreate "test":

df1 <- df1[-which(is.na(test)==TRUE),]
test<-mutate(df1, 
             Q1_1 = as.integer(str_extract(df1$Q1_1,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q1_1)
#After reproducing list of integer extractions from ID column, proceed:

#define "dup" as the location where these duplicates occur
dup <- which(duplicated(test$Q1_1))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(test$Q1_1==test$Q1_1[dup[i]]))),
                      df1$Q1_1[which(test$Q1_1==test$Q1_1[dup[i]])])
}
duplicates
```
   
   
#This output shows us that we have mock data "111", "999", and a discrepancy
arising for subjects "EL001" and "EL017"
   
   
#Check the dates of these duplicates against the original entries
```{r}
#First subject "EL001"
df1$RecordedDate[c(which(df1$Q1_1==duplicates[4,4]),
                   which(df1$Q1_1==duplicates[4,5]))]
#The output shows us that the first entry of subject 
#EL001 occurred in 2015, the other 2017. So delete the second one.
rmEL001 <- which(df1$Q1_1==duplicates[4,5]) #store row number to removed
```
```{r}
#Repeat for "EL017":
df1$RecordedDate[c(which(df1$Q1_1==duplicates[5,4]),
                   which(df1$Q1_1==duplicates[5,5]))]
#The output shows us that the first entry of subject 
#EL017 occurred in 2015, the other 2017. So delete the second one.
rmEL017 <- which(df1$Q1_1==duplicates[5,5]) #store row number to removed
```

#In addition, we need to remove mock/test data with ID # 111 and 999
```{r}
rmMock <- c(which(df1$Q1_1==duplicates[1,5]),
            which(df1$Q1_1==duplicates[2,5]),
            which(df1$Q1_1=="fgh"))
#Okay, now delete all columns identified as above:
df1 <- df1[-c(rmEL001, rmEL017, rmMock),]
```
   
   
#Now standardize the subject ID column:
```{r}
df2 <- df1 %>%
  # extract id NUMBERS only (again)
  mutate(Q1_1 = as.integer(str_extract(df1$Q1_1, 
                                         pattern ="\\(?[0-9,.]+\\)?")))%>%
  # add prefix "EL00", "EL0", or "EL" as necessary; rename:
  mutate(IDENT_SUBID = paste0(ifelse(nchar(Q1_1)==1,"EL00",
                                ifelse(nchar(Q1_1)==2,"EL0",
                                       "EL")), Q1_1)) %>%
  # remove old Q1_1 and return to desired order
  select(RecordedDate,IDENT_SUBID, everything(), -Q1_1)
```

#Convert numeric data to data-type numeric:
```{r}
# factor2numeric <- function(x) {
#   if (class(x) != "factor") {
#     stop(print("Error: variable is not a factor"))
#   } else {
#     as.numeric(as.character(x))
#   }
#   
# }
df3 <- df2 %>% mutate_at(vars(starts_with("Q")), function(x) factor2numeric(x))
```   

#Attach the variable names
```{r}
var_names <- cbind("SS_DATE_COMPLETE", "IDENT_SUBID", "SS_NEW_1A",
                   "SS_NEW_1B","SS_NEW_2A","SS_NEW_2B","SS_NEW_3A",
                   "SS_NEW_3B","SS_NEW_4A","SS_NEW_4B","SS_NEW_5A",
                   "SS_NEW_5B","SS_NEW_6A","SS_NEW_6B","SS_NEW_7A",
                   "SS_NEW_7B","SS_NEW_8A","SS_NEW_8B","SS_NEW_9A",
                   "SS_NEW_9B","SS_NEW_10A","SS_NEW_10B","SS_NEW_11A",
                   "SS_NEW_11B","SS_NEW_12A","SS_NEW_12B","SS_NEW_13A",
                   "SS_NEW_13B","SS_NEW_14A","SS_NEW_14B","SS_NEW_15A",
                   "SS_NEW_15B")
names(df3) <- var_names
```   

#Reformat the date variable to data-type "Date"
```{r}
df4 <- df3 %>% 
  mutate_at(1, function(x) as.character(x)) %>%
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```

#check data-type of all variables, and dimensions
```{r}
#column 1 should be "Date", column 2 "character", all others = "numeric":
classes <- NULL
for (i in var_names) {
    classes[i]<-(select(df4,i))[[1]] %>% class()
}
table(classes)
# #to clarify which variables are which class:
# classes
```

```{R}
#dimensions should be 129 rows and 32 columns for data extracted 3/8/2019
dim(df4)
```

#Check that NAs were prduced from each missing data during tidying process:
```{r}
as.data.frame(where.na(df4))[[1]] == as.data.frame(quantity.missing(df1))[[1]]
#output should all read TRUE
```

##Tidying Complete!
###Write out tidy .Rds, csv and sav files.
```{r}
write_rds(df4,"/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/SS_tidy.Rds")
library(haven)
#convert all fields to character for csv and sav write-out
df5 <- as.data.frame(lapply(df4[,1:ncol(df4)], function(x) as.character(x)),
                     stringsAsFactors = F)
write.csv(df5, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/SS_tidy.csv", row.names = FALSE)
write_sav(df5, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Children/SS_tidy.sav")
```

