---
title: "STAIS Trait tidying"
author: "Ian Douglas"
date: "5/29/2019"
output: html_document
---
#load raw data, extracted 5/29/19
```{r}
rm(list=ls())
suppressPackageStartupMessages(library(tidyverse))
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/STAIS trait.csv", stringsAsFactors = FALSE)
```

#Check for mock/test data
```{r}
head(df$Q1)
tail(df$Q1)
#remove the first two rows
```
Extract desired data
```{r}
df1 <- df[-1:-2,] %>% dplyr::select(RecordedDate, starts_with("Q"))
```
#search for duplicates
```{r}
View(id.search(df1, "Q1", "RecordedDate"))
```
#Fix one typo
EL061 entered "el06lp", causing a conflict with EL006
```{r}
df1$Q1 <- replace(df1$Q1, df1$Q1 == "el06lp", "EL061")
```

For other entries, delete the entry specified below:
```{r}
deletion.matrix <- matrix(c(
  "el070", "2016-12-28 13:02:53", #based on age entered, second (other) entry is correct
"EL079P", "2016-10-16 10:55:52", #this entry comes long after the first (correct), delete
"EL071P", "2017-02-24 13:58:37", #this entry comes long after the first (correct), delete
"EL097", "2017-05-31 12:27:07", #this entry erroneously entered a day after the first
"EL127P", "2018-01-05 13:49:29", #this was the wrong parent of child EL127
"el140", "2018-04-10 13:40:37" #this too after the first (correct), so delete
), ncol = 2, byrow = TRUE)

deletion.indices <- NULL
for (i in 1:nrow(deletion.matrix)) {
  deletion.indices[i] <- which(
    df1$Q1 == deletion.matrix[i,1] & df1$RecordedDate == deletion.matrix[i,2]
  )
}
deletion.indices
df2 <- df1[-deletion.indices,]
```
#format the subject ID and date columns; deselect the user-entered date
```{r}
df3 <- ELFK.identsubid(df2, "Q1") %>% 
  format.date("RecordedDate") %>% 
  select(-Q2_1)
```
#attach the proper variable names
```{r}
vnam <- NULL
for (i in 1:20) {
  vnam[i]<- paste0("PARENT_STAI_TRAIT_",i)
}
names(df3) <- c("PARENT_STAI_TRAIT_DATE","IDENT_SUBID", 
                "PARENT_STAI_TRAIT_AGE","PARENT_STAI_TRAIT_SEX",
                vnam)
```
#ensure numeric data are in correct form
```{r}
# > get.variable.classes(df3)
# classes
# character      Date 
#        23         1 
#convert numeric variables to appropriate format
df4 <- df3 %>%
  mutate_at(grep("[0-9]$", names(.)), as.numeric)
```
Done!
Write out tidy data
```{r}
saveRDS(df4, "/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/02 Tidied/QUALTRICS/Parent/R/STAI_trait_tidy.rds")
```



