---
title: "CBCL tidying"
author: "Ian Douglas"
date: "4/3/2019"
output: html_document
---
#Script for processing the Qualtrics CBCL data
```{r}
rm(list=ls())
df <- read.csv("/Volumes/danl/ELFK/Data_Entry/DATA_ENTRY_MASTER/Data_Merge/01 Raw/QUALTRICS/Parent/CBCL raw.csv", stringsAsFactors = FALSE)
```
#View the first rows of the ID column
```{r}
df$Q3[1:20]
```
#Looks that mock/test data ends at line 8
#Extract desired data
```{r}
#supplant the user-entered date with the timestamp
df1 <- df[9:nrow(df),] %>% select(RecordedDate, starts_with("Q"),-Q5)
```
#Check if any missing data, NA, or if non-numeric subject IDs (or zero's) remain
```{r}
where.na(df1)[2]
quantity.missing(df1)[2]
test<-mutate(df1, 
             Q3 = as.integer(str_extract(df1$Q3,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q3)
which(is.na(test)==TRUE)
which(test==0)
```
#Conclusion: rows 39, 40, and 111 may present problems:
```{r}
df1$Q3[c(39,40,111)]
```
#Indeed, there were more mock data, so delete those as well
```{r}
df2 <- df1[-c(39,40,111),]
```
#Now search for duplicates in the subject ID column
```{r}
digits<-mutate(df2, 
             Q3 = as.integer(str_extract(df2$Q3,pattern ="\\(?[0-9,.]+\\)?"))) %>%
  select(Q3)
#then define "dup"
dup <- which(duplicated(digits$Q3))

#create a side-by-side comparison (2-column matrix with the duplicates)
duplicates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup)),
                           rep(NA_character_,times=length(dup))), 
                     ncol=5)
#now fill it with your values that were duplicated
for (i in 1:length(dup)) {
  duplicates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q3==digits$Q3[dup[i]]))),
                      df2$Q3[which(digits$Q3==digits$Q3[dup[i]])])
}
colnames(duplicates) <- c(rep("Raw entry",times=5))
#duplicates
#Repeat this process with raw dates and raw times.
#create the matrix to capture the date output as well.
dates <- matrix(cbind(rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup)),
                      rep(NA_character_,times=length(dup))), 
                ncol=5)
for (i in 1:length(dup)) {
  dates[i,] <- c(rep(NA_character_, times=ncol(duplicates)-length(which(digits$Q3==digits$Q3[dup[i]]))),
                 as.character(df2$RecordedDate[which(digits$Q3==digits$Q3[dup[i]])]))
}

#combine the matrices and order the columns to see associated info side by side.

search <- cbind(as.data.frame(duplicates),
                as.data.frame(dates))[,c(4,9,5,10)]
names(search) <- c("raw entry #1", "timestamp1","raw entry #2","timestamp2")
search
```
#"EL061" typo'd their subject ID, correct this for them as follows:
```{r}
df2[grep("el06lp",df2$Q3), which(names(df2)=="Q3")] <- "EL061"
```
#Retain the earlier observation of subject "EL142"
```{r}
df3 <- df2[-which(df2$Q3 == "EL142" & df2$RecordedDate == "2018-06-20 09:41:48"),]
```
#Now we are ready to standardize the subject IDs
```{r}
df4 <- ELFK.identsubid(df3,"Q3")
```
#Format the timestamp into data-type Date
```{r}
df5 <- df4 %>% 
  mutate_at(1, function(x) strtrim(x,10)) %>%
  mutate_at(1, function(x) as.Date(x, format = "%Y-%m-%d"))
```

